### 2021-05-11 paper.tex
init

\documentclass[a4paper,12pt]{report}

\usepackage{alltt, fancyvrb, url}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{wrapfig}
\usepackage{algorithmic}
\usepackage[utf8]{inputenc}
\usepackage{fontenc}
\usepackage{amsmath,stmaryrd,mathtools,algorithm}
\usepackage{amssymb}
%\usepackage{amsfonts}
\usepackage{float}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{url}

\usepackage[english]{cleveref}

\usepackage[english]{babel}

\newtheorem{definition}{Definition}[section]
\newcommand{\R}{\mathbb{R}}

\title{Introduction to LLL\\``Cryptography''}

\author{Di Santi Giovanni}
\date{\today}

\begin{document}

\maketitle

\tableofcontents

\chapter{Introduction to Lattices}

\section{Vector Spaces}

\begin{definition}
    \textbf{Vector spaces}.
\end{definition}
A \texttt{vector space} $V$ is a subset of $\R^{m}$ with the property that

\begin{center}
    $\alpha_1v_1 + \alpha_2v_2 + \cdots + \alpha_kv_k$ with $\alpha_1, \ldots, \alpha_k \in \R$
\end{center}

\section{Lattices}

\chapter{LLL}

\section{Purpose}

\section{Algorithm}

\chapter{Applications}

\section{Attack Knapsack}

\section{Attack RSA}

\chapter*{End of Paper}

$gg^2$

\bibliographystyle{plain}
\bibliography{paper}

\end{document}

### 2021-05-25 paper.tex
more definitions of linear alg

@@
 \usepackage{alltt, fancyvrb, url}
+\usepackage{amssymb}
 \usepackage{graphicx}
@@
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\dd}{\cdot}
 
@@
 \begin{definition}
-    \textbf{Vector spaces}.
+    \textbf{Vector space}.
 \end{definition}
-A \texttt{vector space} $V$ is a subset of $\R^{m}$ with the property that
+A \texttt{vector space} $V$ is a subset of $\R^{m}$ which is closed under finite vector addition and scalar multiplication, with the property that
+
+\begin{center}
+   $a_1v_1 + a_2v_2 \in V$ for all $v_1,v_2 \in V$ and all $a_1,a_2 \in \R$
+\end{center}
+
+\begin{definition}
+    \textbf{Linear Combinations}
+\end{definition}
+
+Let $v_1,v_2,\ldots,v_k \in V$. A \texttt{linear combination} of $v_1,v_2,\ldots,v_k \in V$ is any vector of the form
 
@@
     $\alpha_1v_1 + \alpha_2v_2 + \cdots + \alpha_kv_k$ with $\alpha_1, \ldots, \alpha_k \in \R$
+\end{center}
+
+\begin{definition}
+    \textbf{Lineaer Independece}
+\end{definition}
+
+A set of vectors $v_1,v_2,\ldots,v_k \in V$ is \texttt{linearly independent} if the the only way to get
+
+\begin{center}
+    $a_1v_1 + a_2v_2 + \cdots + a_kv_k = 0$
+\end{center}
+
+is to have $a_1 = a_2 = \cdots = a_k = 0$.
+
+\begin{definition}
+    \textbf{Bases}
+\end{definition}
+
+Taken a set of linearly independent vectors $x = (v_1,\ldots,v_n) \in V$ we say that $x$ is a \texttt{basis} of $V$ if $\forall w \in V$ we can write
+
+\begin{center}
+    $w = a_1v_1 + a_2v_2 + \cdots + a_nv_n$
+\end{center}
+
+\begin{definition}
+    \textbf{Vector's length}
+\end{definition}
+
+The vector's length or \texttt{Euclidean norm} of $v = (x_1, x_2, \ldots, x_m)$ is
+
+\begin{center}
+    $\lVert v \rVert = \sqrt{x_1^2 + x_2^2 + \cdots + x_m^2}$
+\end{center}
+
+\begin{definition}
+    \textbf{Dot Product}
+\end{definition}
+
+Let $v, w \in V \subset \R^m$ and $v = (x_1, x_2, \ldots, x_m), w = (y_1, y_2, \ldots, y_m)$, the \texttt{dot product} of $v$ and $m$ is
+
+\begin{center}
+    $v \dd m = x_1y_1 + x_2y_2 + \cdots + x_my_m$
+
+    or
+
+    $v \dd m = \lVert v \rVert \lVert w \rVert \cos{\theta}$
+\end{center}
+
+where $\theta$ is the angle between $v$ and $w$ if we place the starting points of the vectors at the origin $O$.
+
+\begin{figure}[!b]
+    \centering
+    \includegraphics[scale=0.2]{./img/dot_product.png}
+    \caption{Dot Product By 3Blue1Brown}
+    \label{fig:dot_product}
+\end{figure}
+
+Geometrically speaking $v \cdot m$ is the length of $w$ projected to $v$ multiplied by the length of $v$ as shown in \ref{fig:dot_product}
+
+\begin{definition}
+    \textbf{Ortoghonal Basis} 
+\end{definition}
+
+An \texttt{ortoghonal basis} for a vector space $V$ is a basis $v_1, \ldots, v_m$ with the property that
+
+\begin{center}
+    $v_i \dd v_j = 0$ for all $i \neq j$
 \end{center}

### 2021-05-25 paper.tex
add lattice introductions

@@
 \newtheorem{definition}{Definition}[section]
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{property}{Property}[section]
 \newcommand{\R}{\mathbb{R}}
+\newcommand{\Z}{\mathbb{Z}}
 \newcommand{\dd}{\cdot}
@@
 
-Taken a set of linearly independent vectors $x = (v_1,\ldots,v_n) \in V$ we say that $x$ is a \texttt{basis} of $V$ if $\forall w \in V$ we can write
+Taken a set of linearly independent vectors $b = (v_1,\ldots,v_n) \in V$ we say that $b$ is a \texttt{basis} of $V$ if $\forall w \in V$ we can write
 
@@
 
+If $\lVert v_i \rVert = 1$ for all $i$ then the basis is \texttt{orthonormal}.
+
+\begin{theorem}
+    \textbf{Gram-Schmidt Algorithm}
+\end{theorem}
+
+Let $b = (v_1, \ldots, v_n)$, be a basis for a vector space $V \subset \R^m$. There is an algorithm to create an orthogonal basis
+$b^* = (v_1^*,\ldots,v_n^*)$.
+The two bases have the property that Span$\{v_1,\ldots,v_i\}$ = Span$\{v_1^*,\ldots,v_i^*\}$ for all $i = 1,2,\ldots,n$
+
 \section{Lattices}
+
+\begin{definition}
+    \textbf{Lattice}
+\end{definition}
+
+Let $v_1,\ldots,v_n \in \R^m, m \ge n$ be linearly independent vectors. A \texttt{Lattice} $L$ spanned by $\{v_1,\ldots,n_n\}$ is the set of 
+all integer linear combinations of $v_1,\ldots,v_n$.
+
+\begin{center}
+    $L = \bigg\{\sum_{i=1}^{n} a_iv_i, a_i \in \Z \bigg\}$
+\end{center}
+
+If $v_i$ for every $i = 1,\ldots\,n$ has integer coordinates then the lattice is
+called \texttt{Integral Lattice}.
+
+On the figure \ref{fig:lattice1} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$:
+
+\begin{figure}[!b]
+    \centering
+    \includegraphics[width=0.7\textwidth]{./img/lattice.png}
+    \caption{Lattice spanned by $v, w$}
+    \label{fig:lattice1}
+\end{figure}
 

### 2021-05-25 paper.tex
add gram_schmidt plot
Update lattices description and plot

@@
 
+\begin{figure}[htpb]
+    \centering
+    \includegraphics[width=0.5\textwidth]{./img/gram_schmidt.png}
+    \caption{Gram Schmidt orthogonalization}
+    \label{fig:gram_schmidt}
+\end{figure}
+
+If we take $v_1=(4, 1), v_2=(2, 3)$ as basis and apply gram schmidt we obtain $u_1=v_1=(4, 1), u_2=(-10/17, 40/17)$ as shown in \ref{fig:gram_schmidt}
+
 \section{Lattices}
@@
 
-On the figure \ref{fig:lattice1} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$:
+On the figure \ref{fig:lattice0} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$, and on \ref{fig:lattice1} the same lattice $L$ with
+a different basis.
 
-\begin{figure}[!b]
-    \centering
-    \includegraphics[width=0.7\textwidth]{./img/lattice.png}
-    \caption{Lattice spanned by $v, w$}
+\begin{figure}[!tbp]
+    \begin{minipage}[b]{0.50\textwidth}
+        \includegraphics[width=\textwidth]{./img/lattice_b0.png}
+        \caption{Lattice $L$ of $v, w$}
+        \label{fig:lattice0}
+    \end{minipage}
+    \hspace{\fill}
+    \hspace{\fill}
+    \hspace{\fill}
+    \hspace{\fill}
+    \hspace{\fill}
+    \begin{minipage}[b]{0.50\textwidth}
+        \includegraphics[width=\textwidth]{./img/lattice_b1.png}
+        \caption{Lattice $L$ of $v', w'$}
         \label{fig:lattice1}
+    \end{minipage}
 \end{figure}
 
+% matrix([[0, 0, 1], [1, 1, 2], [1, 2, 1]])
 \chapter{LLL}

### 2021-05-26 paper.tex
Add SVP and CVP

@@
 
-\begin{theorem}
+\begin{algorithm}
     \textbf{Gram-Schmidt Algorithm}
-\end{theorem}
+\end{algorithm}
 
@@
         \includegraphics[width=\textwidth]{./img/lattice_b0.png}
-        \caption{Lattice $L$ of $v, w$}
+        \caption{Lattice $L$ spanned by $v, w$}
         \label{fig:lattice0}
@@
         \includegraphics[width=\textwidth]{./img/lattice_b1.png}
-        \caption{Lattice $L$ of $v', w'$}
+        \caption{Lattice $L$ spanned by $v', w'$}
         \label{fig:lattice1}
     \end{minipage}
+\end{figure}
+
+\section{Problems}
+
+\subsection{SVP}
+
+\textbf{The Shortest Vector Problem} (\texttt{SVP}): Find a nonzero vector $v \in L$ that minimez the Euclidean norm $\lVert v \rVert$.
+
+\begin{algorithm}
+    \textbf{Gauss Reduction}
+\end{algorithm}
+
+Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
+gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.
+
+If we take for example $v_1 = (10, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
+obtain $w_1 = (3, -1), w_2 = (4, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.
+
+\begin{figure}[b]
+    \centering
+    \includegraphics[width=0.5\textwidth]{./img/gauss_svp.png}
+    \caption{Gauss reduction}
+    \label{fig:gauss_svp}
+\end{figure}
+
+However the bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to find such vector.
+
+\subsection{CVP}
+
+\textbf{The Closest Vector Problem} (\texttt{CVP}): Given a vector $w \in \R^m$ that is not in $L$, find a vector $v \in L$ that is closest to $w$,
+in other words find a vector $v \in L$ that minimizes the Euclidean norm $\lVert w - v \rVert$.
+
+Example in \ref{fig:cvp}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=0.5\textwidth]{./img/cvp.png}
+    \caption{CVP}
+    \label{fig:cvp}
 \end{figure}

### 2021-05-26 paper.tex
Intro to LLL

@@
 
-\chapter{Introduction to Lattices}
+\chapter{Linear Algebra Background}
 
@@
 
-Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
-gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.
-
-If we take for example $v_1 = (10, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
-obtain $w_1 = (3, -1), w_2 = (4, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.
-
 \begin{figure}[b]
@@
 \end{figure}
+
+Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
+gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.
+
+If we take for example $v_1 = (10, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
+obtain $w_1 = (3, -1), w_2 = (4, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.
 
@@
 
+TODO: CVP and SVP are related.
+
 % matrix([[0, 0, 1], [1, 1, 2], [1, 2, 1]])
@@
 
-\section{Purpose}
+\section{Introduction}
+
+The \textbf{Lenstra-Lenstra-Lovász} \textit{LLL} or \textit{$L^3$} is a polynomial time algorithm to find a "shorter" basis.
+
+\begin{theorem}
+    \textbf{LLL}
+\end{theorem}
+
+\textit{Let $L \in \Z^n$ be a lattice spanned by $B = \{v_1,\ldots,v_n\}$. The LLL algorithm outputs a reduced lattice
+basis $\{w_1, \ldots, w_n\}$ with}
+
+\begin{center}
+    $\lVert w_i \rVert \le 2^{\frac{n(n-1)}{4(n-i+1)}} det(L)^{\frac{1}{n-i+1}}$ for $i=1,\ldots,n$
+\end{center}
+
+\textit{in time polynomial in n and in the bit-size of the entries of the basis matrix $B$}.\\
+
+Basically the first vector of the new basis will be as short as possible, and the other will have increasing lengths. The new vectors
+will be as orthogonal as possible to one another, i.e., the dot product $w_i \dd w_j$ will be close to zero.
+
+\subsection*{Example}
+
+For example we can take the following basis (the rows are the vector) that span
+a lattice $L$.
+
+\[
+L = 
+\begin{pmatrix}
+    4 & 9 & 10\\
+    2 & 1 & 30\\ 
+    3 & 7 & 9
+\end{pmatrix}
+\]
+
+Applying the LLL algorithm we obtain
+
+\[
+LLL(L) = 
+\begin{pmatrix}
+    -1 & -2 & -1\\
+     3 & -2 &  1\\
+    -1 & -1 &  5
+\end{pmatrix}
+\]
+
+Where the first row is the shortest vector in the lattice $L$, and so solves the \textbf{SVP} problem.
+For higher dimensions however the LLL algorithm outputs only an approximation for the \textbf{SVP} problem.
 
 \section{Algorithm}
+
+TODO: Write algorithm and explain some steps
+
+\section{Applications}
+
+There are many applications of LLL
+
+\begin{enumerate}
+    \item Factoring polynomials over the integers. For example, given $x^2 - 1$ factor it into $x + 1$ and $x - 1$.
+    \item Integer Programming. This is a well-known \textbf{NP}-complete problem. Using LLL, one can obtain a polynomial time solution
+          to integer programming with a fixed number of variables.
+    \item Approximation to the \textbf{CVP} or \textbf{SVP}, as well as other lattice problems.
+    \item Application in cryptanalysis.
+\end{enumerate}
 

### 2021-05-27 paper.tex
Init RSA Attack

@@
 
-\chapter{Applications}
+\chapter{Cryptanlysis}
 
-\section{Attack Knapsack}
+% \section{Attack Knapsack}
 
-\section{Attack RSA}
+\section{RSA introduction}
+
+\textbf{RSA} is one of the earliest and most used asymmetric cryptosystem.
+The usual step to generate a public/private key for \textbf{RSA} is the following
+
+\begin{enumerate}
+    \item Fix $e = 65537$ or $e = 3$ (public).
+    \item Find two primes $p, q$ such that $p - 1$ and $q - 1$ are relatively prime to $e$, i.e. gcd$(e, p-1) = 1$ and gcd$(e, q-1) = 1$.
+    \item Compute $N = p * q$ and $\phi(n) = (p-1) * (q-1)$
+    \item Calculate $d$ (private) as the multiplicative inverse of $e$ modulo $\phi(n)$.
+    \item $(N, e)$ is the public key, $(N, d)$ is the private key.
+\end{enumerate}
+
+To encrypt a message $m$ with \textbf{textbook RSA}
+
+\begin{center}
+    $c = m^e \mod N$
+\end{center}
+
+To decrypt a ciphertext $c$
+
+\begin{center}
+    $m = c^d \mod N$
+\end{center}
+
+\section{Lattices against RSA}
+
+It's easy to find the roots of a univariate polynomial over the integers. Finding the roots of \textbf{modular} polynomial is hard, example:
+
+\begin{center}
+    $f(x) \equiv 0 \mod N$
+\end{center}
+
+Suppose $N$ is an \textbf{RSA} modulus and we don't know the factorization of it. Let's have an univariate integer polynomial $f(x)$ with degree $n$
+
+\begin{center}
+    $f(x) = x^n + a_{n-1}x^{n-1} + a_{n-2}x^{n-2} + \cdots + a_1n + a_0$
+\end{center}
+
+Coppersmith showed how we can recover the value $x_0$ such that $f(x_0) \equiv 0 \mod N$, with $x_0 < N^{\frac{1}{n}}$ in polynomial time
+using the following theorem
+
+\begin{theorem}
+    \textbf{Howgrave-Graham}
+\end{theorem}
+
+\textit{Let $g(x)$ be an univariate polynomial with n monomials and $m$ be a positive integer.
+    If we have some restraint $X$ and the following equations hold}
+
+\begin{center}
+    \begin{eqnarray}
+         g(x_0) \equiv 0 \mod N^m, |x_0| \le X \\
+         \lVert g(xX) \rVert < \frac{N}{\sqrt{n}} \label{eq:pol}
+    \end{eqnarray}
+\end{center}
+
+Then $g(x_0) = 0$ holds over the integers.
+
+\subsection{Example}
+
+We have a 100-bit \textbf{RSA} modulus
+
+\begin{center}
+    $N=0xf046522fb555a90bdc558fc93$ and $e = 3$.
+\end{center}
+
+Before the encryption the message $m$ is padded as
+
+\[
+    z = pad || m = 0x74686973206b65793a00 || m
+\]
+
+where $||$ is the concatenation.\\
+
+The ciphertext is
+
+\[
+    c = z^e \mod N = 0x8185d7de1d7cb8801e69c0bf
+\]
+
+Suppose that we don't know the factorization of $N$ and we would like to know the message $m$.
+However we know the padding and the length of $m < 2^{16}$.
+
+\vspace*{10px}
+
+Let's define
+
+\[
+a = 0x74686973206b65793a0000
+.\]
+
+which is the known padding string.
+
+\vspace*{10px}
+
+Thus we have that $c = (a + m)^3 \mod N$, for an unkown small $m$.
+We can define $f(x) = (a + x)^3 - c$, and so we setup the problem to find a small root $m$ such that $f(m) \equiv 0 \mod N$
+
+\begin{align*}
+    f(x) = x^3 + 0x15d393c596142306bae0000x^2 + 0x1b53c5e184a49b39f9ad9eedbx \\
+    + 0x9bb23cefd94fac9cc9cee9943
+\end{align*}
+
+\vspace*{10px}
+
+\textbf{Lattice contruction}. Let the coefficients of $f$ be $f(x) = x^3 + f_2x^2 + f_1x + f_0$
+and $X = 2^{16}$ be the upper bound of the size of the root $m$. We can construct the matrix
+
+\[
+B = 
+\begin{pmatrix}
+    X^3 & f_2X^2 & f_1X & f_0 \\
+    0 & NX^2 & 0 & 0 \\
+    0 & 0 & NX & 0 \\
+    0 & 0 & 0 & N \\
+\end{pmatrix}
+\]
+
+If we apply LLL to the lattice we get
+
+\clearpage
+We can use lattices to solves the problem:
+
+\begin{itemize}
+    \item If we have some polynomial which share the same root $x_0$ over $N^m$ we can represent each of them as a row from lattice,
+        and every linear integer combination of rows between them will yield another polynomial having a root $x_0$.
+    \item Using \textbf{LLL} on the lattice we can find a reduced lattice basis, such that the norm of the shortest vector will
+        satisfy the inequality of \ref{eq:pol}. \textbf{LLL} will only use \textbf{linear integer operations} on the basis vectors,
+        in this way we preserve the root $x_0$ and the bound $X$.
+    \item Define the shortest vector in the reduced basis as $v = (v_0, v_1, \ldots, v_n)$. We can construct the polynomial
+        \begin{center}
+            \[
+                g(x) = v_0 + \frac{\displaystyle v_1}{X}x + \frac{v_2}{X^2}x^2 + \cdots + \frac{v_n}{X^n}x^n
+            \]
+        \end{center}
+\end{itemize}
+Since $g(x)$ is on the lattice we know that
+
+\begin{center}
+    \begin{eqnarray}
+        g(x_0) \equiv 0 \mod N^m \\
+        \vert x_0| \le X \\
+        \lVert g(xX) \rVert < \frac{N^m}{\sqrt{deg(g) + 1}}
+    \end{eqnarray}
+\end{center}
+
+\section{Key recovery ECDSA}
 

### 2021-05-27 paper.tex
RSA Attack TODO: modify parameter

@@
     \begin{eqnarray}
-         g(x_0) \equiv 0 \mod N^m, |x_0| \le X \\
+        g(x_0) \equiv 0 \mod N^m, |x_0| \le X \label{eq:bound} \\
          \lVert g(xX) \rVert < \frac{N}{\sqrt{n}} \label{eq:pol}
@@
 
-Then $g(x_0) = 0$ holds over the integers.
+\textit{Then $g(x_0) = 0$ holds over the integers.}
+
+\vspace*{10px}
+
+This theorem states that is possible to compute the root of $f(x) \mod N$ if we can find a polynomial $g(x)$ that share the same root but modulo $N^m$.
+If \ref{eq:bound} and \ref{eq:pol} hold then we can simply compute the root of $g(x)$ over the integers to have the same root $x_0$
+such that $f(x_0) \equiv 0 \mod N$.
+
+Howgrave-Graham's idea is to find this polynomial $g$ by combining polynomials $g_{i,j}$ who also have $x_0$ as roots modulo $N^m$.
+
+\vspace*{10px}
+
+The \textbf{LLL} algorithm is fundamental because:
+
+\begin{itemize}
+    \item It only does \textbf{integer linear operations} on the basis vectors.
+        In this way even if the basis is different it's only a linear combination of vector that still have $x_0$ as root
+        modulo $N^m$.
+    \item If we craft the lattice properly, the norm of shortest vector on the reduced basis will satisfy \ref{eq:pol}.
+\end{itemize}
+
+We can easily create polynomials $p_i$ ($g_{i,j}$ and $h_i$)  sharing the same root $x_0$ over $N^m$ of $f$ where $\delta$ is the degree of $f$:
+
+\begin{center}
+    \begin{eqnarray}
+        g_{i,j}(x) &= x^j \cdot N^i \cdot f^{m-i}(x) \text{ for } i = 0,\hdots,m-1,\hspace{2mm} j=0,\hdots,\delta-1 \label{eq:create_pol} \\
+        h_i(x) &= x^i \cdot f^m(x) \text{ for } i = 0,\hdots,t-1 
+    \end{eqnarray}
+\end{center}
 
@@
 Suppose that we don't know the factorization of $N$ and we would like to know the message $m$.
-However we know the padding and the length of $m < 2^{16}$.
+However we know the padding and that the length of $m < 2^{16}$.
 
@@
 
-which is the known padding string.
+which is the known padding string that got encrypted.
 
@@
 \begin{align*}
-    f(x) = x^3 + 0x15d393c596142306bae0000x^2 + 0x1b53c5e184a49b39f9ad9eedbx \\
-    + 0x9bb23cefd94fac9cc9cee9943
+    f(x) = x^3 + 0x15d393c596142306bae000000x^2 + 0x969acdb25c5f7b5ff7f29bc59x \\
+    + 0x75abf10edc37c4b90c5897322
 \end{align*}
@@
 
-If we apply LLL to the lattice we get
+The rows of the matrix correspond to the coefficient vectors of the polynomials $f(x), Nx^2, Nx$ and $N$, furthermore we know
+that each polynomials will be 0 modulo $N$ if evaluated at $x = m$.
+We didn't fully applied Howgrave-Graham because we only used $m=1$ (the $N^m$ parameter not the message).\\
+With this lattice construction every vector is of the form $v = (v_1X^3, v_2X^2, v_1X, v_0)$, because any
+integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=0,..,\dim(B)-1$.
 
-\clearpage
-We can use lattices to solves the problem:
+\textbf{Apply LLL}. We then apply LLL to find the shortest vector of the reduced basis:
 
-\begin{itemize}
-    \item If we have some polynomial which share the same root $x_0$ over $N^m$ we can represent each of them as a row from lattice,
-        and every linear integer combination of rows between them will yield another polynomial having a root $x_0$.
-    \item Using \textbf{LLL} on the lattice we can find a reduced lattice basis, such that the norm of the shortest vector will
-        satisfy the inequality of \ref{eq:pol}. \textbf{LLL} will only use \textbf{linear integer operations} on the basis vectors,
-        in this way we preserve the root $x_0$ and the bound $X$.
-    \item Define the shortest vector in the reduced basis as $v = (v_0, v_1, \ldots, v_n)$. We can construct the polynomial
-        \begin{center}
 \[
-                g(x) = v_0 + \frac{\displaystyle v_1}{X}x + \frac{v_2}{X^2}x^2 + \cdots + \frac{v_n}{X^n}x^n
+    \begin{split}
+    v = (0x24409ad85f781X^3, -0xd75ab858b980X^2, \\
+        0x1973847f4ddb8X, -0x9a2d87b43d)
+    \end{split}
 \]
-        \end{center}
-\end{itemize}
-Since $g(x)$ is on the lattice we know that
 
-\begin{center}
-    \begin{eqnarray}
-        g(x_0) \equiv 0 \mod N^m \\
-        \vert x_0| \le X \\
-        \lVert g(xX) \rVert < \frac{N^m}{\sqrt{deg(g) + 1}}
-    \end{eqnarray}
-\end{center}
+We can construct the polynomial $g$ using the coefficients of $v$
+
+\[
+    \begin{split}
+        g(x) = 0x24409ad85f781x^3  - 0xd75ab858b980x^2 \\ 
+        + 0x1973847f4ddb8x - 0x9a2d87b43d
+    \end{split}
+\]
+
+We know that
+
+\[
+    g(x_0) \equiv 0 \mod N, |x_0| \le X
+\]
+
+What we need to prove is that
+
+\[
+    \lVert g(xX) \rVert \le \frac{N}{\sqrt{n+1}}
+\]
+
+In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 1.02^n (\det B)^{\frac{1}{dimB}}$.
+If we ignore the $1.02^n$ factor, then we need to satisfy that
+
+\[
+    g(m) \le \lVert v \rVert \le (\det B)^{\frac{1}{4}} < X
+\]
+
+\vspace*{10px}
+
+We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < N$, if we solves for $X$ this will be satisfied when $X < N^{\frac{1}{6}}$.
+In this case we have $N = 100$-bit number and $X = 2^{16}$, so $N^{\frac{1}{6}} > X$ and we have verified the correctness.\\
+
+If we compute the root of $g(x)$ over the integers we obtain $m = 0x61$ which is the correct result.\\
+
+If you want to find bigger root you need to create a bigger lattice with more polynomials generated with \ref{eq:create_pol},
+this method is better described in TODO.
 

### 2021-05-27 paper.tex
Implementation of RSA Attack for 1024 bit modulus

@@
 \[
-    z = pad || m = 0x74686973206b65793a00 || m
+    z = pad || m = 0x74686973206b65793a || m
 \]
 
-where $||$ is the concatenation.\\
+where $||$ is the concatenation. The padding is the ascii encoding of ``this key:''\\
 
@@
 \[
-    c = z^e \mod N = 0x8185d7de1d7cb8801e69c0bf
+    c = z^e \mod N = 0x5b603cda4b72100c6f25954fc
 \]
@@
 \begin{align*}
-    f(x) = x^3 + 0x15d393c596142306bae000000x^2 + 0x969acdb25c5f7b5ff7f29bc59x \\
-    + 0x75abf10edc37c4b90c5897322
+    f(x) = x^3 + 0x15d393c596142306bae0000x^2 + 0x1b53c5e184a49b39f9ad9eedbx\\
+    + 0x486a5d936fb568185c8ff0506
 \end{align*}
@@
     \begin{split}
-    v = (0x24409ad85f781X^3, -0xd75ab858b980X^2, \\
-        0x1973847f4ddb8X, -0x9a2d87b43d)
+    v = (0x90843131bc53X^3 + 0x2736f60b1c7ba3294X^2, \\
+    -0x1bec331b20625341b6d73X, 0x47336b98335c143ac912ec9e)
     \end{split}
@@
     \begin{split}
-        g(x) = 0x24409ad85f781x^3  - 0xd75ab858b980x^2 \\ 
-        + 0x1973847f4ddb8x - 0x9a2d87b43d
+        g(x) = 0x90843131bc53x^3 + 0x2736f60b1c7ba3294x^2 \\
+        -0x1bec331b20625341b6d73x + 0x47336b98335c143ac912ec9e
     \end{split}
@@
 
-If we compute the root of $g(x)$ over the integers we obtain $m = 0x61$ which is the correct result.\\
+If we compute the root of $g(x)$ over the integers we obtain $m = 0x6162$ which is the correct result.\\
+
+This specific lattice works to find roots up to size $N^{\frac{1}{6}}$, so the same construction will work if we want to find
+
+\begin{itemize}
+    \item \textasciitilde 170 unkown bits of message from an RSA 1024-bit modulus
+    \item \textasciitilde 341 unkown bits of message from an RSA 2048-bit modulus
+    \item \textasciitilde 683 unkown bits of message from an RSA 4096-bit modulus
+\end{itemize}
 
 If you want to find bigger root you need to create a bigger lattice with more polynomials generated with \ref{eq:create_pol},
-this method is better described in TODO.
+this method is better described in TODO, but the principles are the same.
 

### 2021-05-27 paper.tex
Fix gauss svp image

@@
 
-If we take for example $v_1 = (10, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
-obtain $w_1 = (3, -1), w_2 = (4, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.
+If we take for example $v_1 = (8, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
+obtain $w_1 = (1, -1), w_2 = (6, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.
 
@@
 
-Example in \ref{fig:cvp}
+TODO FIX \ref{fig:cvp} is wrong, the lattice is different.
 

### 2021-05-31 paper.tex
Fix computation of bounds for LLL vs RSA
TODO: Fix numbers with new ones

@@
 
+\subsection{Algorithm}
+
 \textbf{RSA} is one of the earliest and most used asymmetric cryptosystem.
@@
 
+\subsection{Security}
+
+RSA relies on the hardness of factoring the modulo $N$ and we don't have a polynomial algorithm to factor it, so it's considered secure.
+However there are different attacks against textbook RSA or a relaxed model of RSA:
+
+\begin{enumerate}
+    \item If $m < N^{\frac{1}{e}}$, then $m^e < N$ and the modulo operation is not applied and we only need to find the $e$th root of $c$ over the
+        integers to find $m$.
+    \item If $q = p + x$ where $x$ is small enough than it's easy to recover the factors of $N$ computing $A = \sqrt{N}$ and compute
+            $p = A - x$ for different value of $x$ until $N \mod p = 0$, then we have found $q = N / p$
+    \item Many more attacks can be found TODO.
+\end{enumerate}
+
 \section{Lattices against RSA}
+
+We want to attack a relaxed model of RSA where we know a part of the message $m$.
+We start introducing the \ref{TODO} coppersmith attack and the math behind it.
+
+\subsection{Mathematical introduction}
 
@@
         g(x_0) \equiv 0 \mod N^m, |x_0| \le X \label{eq:bound} \\
-         \lVert g(xX) \rVert < \frac{N}{\sqrt{n}} \label{eq:pol}
+         \lVert g(xX) \rVert < \frac{N^m}{\sqrt{n}} \label{eq:pol}
     \end{eqnarray}
@@
 
-Howgrave-Graham's idea is to find this polynomial $g$ by combining polynomials $g_{i,j}$ who also have $x_0$ as roots modulo $N^m$.
+Howgrave-Graham's idea is to find this polynomial $g$ by combining polynomials $p_i$ who also have $x_0$ as roots modulo $N^m$.
 
@@
     \item If we craft the lattice properly, the norm of shortest vector on the reduced basis will satisfy \ref{eq:pol}.
+        We know the length's bound of the shortest vector that LLL could find.
 \end{itemize}
@@
 that each polynomials will be 0 modulo $N$ if evaluated at $x = m$.
-We didn't fully applied Howgrave-Graham because we only used $m=1$ (the $N^m$ parameter not the message).\\
+We applied Howgrave-Graham with $m=1$ (the $N^m$ parameter not the message).\\
 With this lattice construction every vector is of the form $v = (v_1X^3, v_2X^2, v_1X, v_0)$, because any
@@
 \[
-    \lVert g(xX) \rVert \le \frac{N}{\sqrt{n+1}}
+    \lVert g(xX) \rVert \le \frac{N}{\sqrt{n}}
 \]
 
-In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 1.02^n (\det B)^{\frac{1}{dimB}}$.
-If we ignore the $1.02^n$ factor, then we need to satisfy that
+In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 2^{\frac{n(n-1)}{4(n)}} (\det B)^{\frac{1}{n}}$.
+If we ignore the $2^{\frac{3}{4}}$ factor (remember that $n = 4$), then we need to satisfy that
 
 \[
-    g(m) \le \lVert v \rVert \le (\det B)^{\frac{1}{4}} < X
+    g(m) \le \lVert v \rVert \le (\det B)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}
 \]
@@
 
-We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < N$, if we solves for $X$ this will be satisfied when $X < N^{\frac{1}{6}}$.
-In this case we have $N = 100$-bit number and $X = 2^{16}$, so $N^{\frac{1}{6}} > X$ and we have verified the correctness.\\
+We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solves for $X$ this will be satisfied when $X < (\frac{N}{16})^{\frac{1}{6}}$.
+With the numbers we have this inequality is verified, however even if the bound of the shortest vector is larger we still have some possibilities to
+find the correct root.
 

### 2021-05-31 paper.tex
Better explanation of coppersmith rsa

@@
 
+Applying \textbf{LLL} to a lattice constructed by the coefficients of \ref{eq:create_pol} we'll find a short vector $v = g(xX)$ that will
+satisfy \ref{eq:pol}. If we then take $g(x)$ we will be able to compute the root over the integer.
+
 \subsection{Example}
@@
 In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 2^{\frac{n(n-1)}{4(n)}} (\det B)^{\frac{1}{n}}$.
-If we ignore the $2^{\frac{3}{4}}$ factor (remember that $n = 4$), then we need to satisfy that
+If we ignore the $2^{\frac{3}{4}}$ factor (remember that $n = 4$), then we need to satisfy
 
@@
 
-If you want to find bigger root you need to create a bigger lattice with more polynomials generated with \ref{eq:create_pol},
+To compute bigger root a bigger lattice with more polynomials generated with \ref{eq:create_pol} is needed,
 this method is better described in TODO, but the principles are the same.

### 2021-06-01 paper.tex
ECDSA intro

@@
 
-\section{RSA introduction}
+\section{RSA Introduction}
 
@@
 
-\section{Key recovery ECDSA}
+\section{ECDSA Introduction}
+
+\subsection{Algorithm}
+
+\textbf{ECDSA} is a variant of the Digital Signature Algorithm (\textbf{DSA}) which uses elliptic curve cryptography.
+To digitally sign a message we have 3 public parameters
+
+\begin{itemize}
+    \item The elliptic curve \textbf{$E$}.
+    \item The generator point \textbf{$G$}.
+    \item The generator's order \textbf{$n$}.
+\end{itemize}
+
+We also need to create a private key $d \in [1, n-1]$ and public key $Q = dG$. To digitally \textbf{sign} a message $m$:
+
+\begin{enumerate}
+    \item Compute $h = $ HASH$(m)$ where HASH is a cryptographic hash functions.
+    \item Select a random integer $k \in [1, n-1]$.
+    \item Calculate $P = kG = (x_1, y_1)$ and set $r = (x_1)$.
+    \item Compute $s = k^{-1}(h + dr) \mod n$.
+\end{enumerate}
+
+\vspace*{10px}
+
+To \textbf{verify} the signature:
+
+\begin{enumerate}
+    \item Compute $h = $ HASH$(m)$.
+    \item Calculate $u_1 = hs^{-1} \mod n$ and $u_2 = rs^{-1} \mod n$.
+    \item Compute $P = u_1G + u_2Q = (x_1, y_1)$.
+    \item If $r \equiv x_1 \mod n$ then the signature is valid.
+\end{enumerate}
+
+\subsection{Security}
+
+\section{Lattices against ECDSA}
+
+\subsection{Example}
 

### 2021-06-01 paper.tex
ECDSA attack intro explained

@@
 \newcommand{\Z}{\mathbb{Z}}
+\newcommand{\F}{\mathbb{F}}
 \newcommand{\dd}{\cdot}
@@
 RSA relies on the hardness of factoring the modulo $N$ and we don't have a polynomial algorithm to factor it, so it's considered secure.
-However there are different attacks against textbook RSA or a relaxed model of RSA:
+However there are different attacks against textbook RSA or bad implementations:
 
-\begin{enumerate}
+\begin{itemize}
     \item If $m < N^{\frac{1}{e}}$, then $m^e < N$ and the modulo operation is not applied and we only need to find the $e$th root of $c$ over the
@@
     \item Many more attacks can be found TODO.
-\end{enumerate}
+\end{itemize}
 
@@
     \item Calculate $P = kG = (x_1, y_1)$ and set $r = (x_1)$.
-    \item Compute $s = k^{-1}(h + dr) \mod n$.
+    \item Compute $s = k^{-1}(h + dr) \mod n$, if $s = 0$ repeat the steps.
+    \item The signature is composed by $(r, s)$.
 \end{enumerate}
@@
     \item Calculate $u_1 = hs^{-1} \mod n$ and $u_2 = rs^{-1} \mod n$.
-    \item Compute $P = u_1G + u_2Q = (x_1, y_1)$.
+    \item Compute $P = u_1G + u_2Q = (x_1, y_1)$, if $P = O$ the signature is invalid.
     \item If $r \equiv x_1 \mod n$ then the signature is valid.
@@
 
+The security of \textbf{ECDSA} depends on the discrete logarithm problem.
+Given the points $Q, G$ such that $Q = k*G$ it's considered an hard problem to find $k$.
+However as RSA there are lots of implementation attacks
+
+\begin{itemize}
+    \item If the same $k$ is used to generate two different signatures it's possible to recover the secret key $d$. This was a real bug 
+        discovered in the Playstation 3.
+    \item It's possible to recover $d$ if the parameter $k$ is not generated with a cryptographically secure pseudo random generator.
+    \item If the elliptic curve used is not standardized (custom) then it's possible that the discrete logarithm is easily solvable.
+\end{itemize}
+
 \section{Lattices against ECDSA}
@@
 \subsection{Example}
+
+Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
+$G = (\texttt{0xcc3b3d1a0c4938ef}, \texttt{0x4ab35ff66f8194fa})$ with order $n = \texttt{0xfffffffefa23f437}$.
+
+\vspace*{10px}
+
+We have two signature:
+
+\[
+    \begin{array}{c}
+        (r_1, s_1) = (\texttt{0x269fa43451c5ff3c}, \texttt{0x1184ec0a74d4be7c}) \\
+        \text{and hash } h_1 = \texttt{0xb526aef1a341cfe6}
+    \end{array}
+\]
+
+\[
+    \begin{array}{c}
+        (r_2, s_2) = (\texttt{0xf77cda14f5bf50a2}, \texttt{0xcd1143ccc1516b02}) \\ 
+        \text{and hash } h_2 = \texttt{0x84768ddee659efea}
+    \end{array}
+\]
+
+And we know that both of these signatures use 32-bit nonce $k$, note that $n$ is a 64-bit number. We can set up the problem as a system of equation
+
+\[
+    \begin{array}{c}
+        s_1 \equiv \displaystyle\frac{h_1 + dr_1}{k_1} \mod n \\ \\ 
+        s_2 \equiv \displaystyle\frac{h_2 + dr_2}{k_2} \mod n
+    \end{array}
+\]
+
+We don't know $d, k_1, k_2$, but we can write
+
+\[
+    d = \displaystyle\frac{s_1k_1 - h_1}{r_1}
+\]
+
+and rewrite the equation in
+
+\[
+    k_1 - s_1^{-1}s_2r_1^{-1}k_2 + s_1^{-1}r_1h_2r_2^{-1} - s_1^{-1}h_1 \equiv 0 \mod n
+\]
+
+To simplify the equation we write $t = - s_1^{-1}s_2r_1^{-1}k_2$ and $u = s_1^{-1}r_1h_2r_2^{-1} - s_1^{-1}h_1$. In this way we have
+
+\[
+    \begin{array}{c}
+        k_1 + tk_2 + u \equiv 0 \mod n \\
+        \text{or} \\
+        -k_1 = tk_2 + u - xn \text{   for some $x$}
+    \end{array}
+\]
+
+We know that $|k_1|, |k_2| < K = 2^{32}$.
+
+\vspace*{10px}
+
+\textbf{Lattice construction}. We construct the lattice
+
+\[
+    B = 
+    \begin{pmatrix}
+        n & 0 & 0 \\
+        t & 1 & 0 \\
+        u & 0 & K \\
+    \end{pmatrix}
+\]
+
+The vector $v = (-k_1, k_2, K)$ is in the lattice because
+
+\[
+    v = (tk_2 + u - xn = -k_1, k_2, K)
+\]
+
+for some $x, k_1, k_2 \in Z$.
 

### 2021-06-01 paper.tex
ECDSA attack explained 1st part

@@
 Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
-$G = (\texttt{0xcc3b3d1a0c4938ef}, \texttt{0x4ab35ff66f8194fa})$ with order $n = \texttt{0xfffffffefa23f437}$.
+$G = (\texttt{0xcc3b3d1a0c4938ef}, \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.
 
@@
 
-for some $x, k_1, k_2 \in Z$.
+for some $x, k_2 \in Z$.
 
-\chapter*{End of Paper}
+\vspace*{10px}
+
+Can we prove that $v$ is a short vector that we can find with LLL?
+
+We have
+
+\begin{center}
+    $\lVert v \rVert = \sqrt{k_1^2 + k_2^2 + K^2} \le \sqrt{3K^2} = \sqrt{3}K $
+\end{center}
+
+And we expect the shortest vector to have length
+
+\[
+    \begin{array}{c}
+        \approx 2^{\frac{1}{2}}(\det B)^{\frac{1}{3}} \\
+        \approx 2^{\frac{1}{2}}(nK)^{\frac{1}{3}}
+    \end{array}
+\]
+
+So we want that
+
+\begin{center}
+    $\lVert v \rVert \le \sqrt{3}K < \sqrt{2}(nK)^{\frac{1}{3}}$
+\end{center}
+
+And if we remove the smaller terms this will be satisfied when $K < (nK)^{\frac{1}{3}}$ or $K < \sqrt{n}$.
+
+This method is described better in
+
+%Boneh-Venkatesan1996_Chapter_HardnessOfComputingTheMostSign-1.pdf, HPL-1999-90-1.pdf, https://www.researchgate.net/publication/2406712_The_Insecurity_of_the_Elliptic_Curve_Digital_Signature_Algorithm_with_Partially_Known_Nonces
+
+\chapter*{Conclusion}
 

### 2021-06-02 paper.tex
Implement ECDSA attack with lots of nonce
ECDSA attack explained known bits nonce

@@
     0 & 0 & NX & 0 \\
-    0 & 0 & 0 & N \\
+    0 & 0 & 0 & N
 \end{pmatrix}
@@
 
-\subsection{Example}
+\subsection{Recover $d$ from a pair of signatures with small $k_1, k_2$}
 
@@
 
-\textbf{Lattice construction}. We construct the lattice
+\textbf{Lattice construction}. We construct the lattice $B = (b_0, b_1, b_2)$:
 
@@
         t & 1 & 0 \\
-        u & 0 & K \\
+        u & 0 & K
     \end{pmatrix}
@@
 
-The vector $v = (-k_1, k_2, K)$ is in the lattice because
+Note that the vector $v = (-k_1, k_2, K)$ is in the lattice because
 
 \[
-    v = (tk_2 + u - xn = -k_1, k_2, K)
+    v = -xb_0 + k_2b_1 + b_2 = (-xn + tk_2 + u = -k_1, k_2, K)
 \]
@@
 
-This method is described better in
+In this case if we apply LLL in the second row we obtain:
+
+\begin{center}
+    $v = (-k_1, k_2, K) = (\texttt{-0x50a65330, 0x1f5b977a, 0x100000000})$
+\end{center}
+
+To retrieve $d$ we just need to compute
+
+\[
+    d = r_1^{-1}(k_1s_1 - h_1) = \texttt{0xf00e5fb275bfd304}
+\]
+
+Source of the method:
 
 %Boneh-Venkatesan1996_Chapter_HardnessOfComputingTheMostSign-1.pdf, HPL-1999-90-1.pdf, https://www.researchgate.net/publication/2406712_The_Insecurity_of_the_Elliptic_Curve_Digital_Signature_Algorithm_with_Partially_Known_Nonces
+
+\subsection{Recover $d$ from many signatures}
+
+Suppose we have many signatures $(r_1, s_1), \ldots, (r_m, s_m)$ with message hashes $h_1, \ldots, h_m$. We can write the equivalence
+$s_i \equiv k_i^{-1}(h_i +  dr_i) \mod n$ for $i = 1,\ldots,m$ and we can remove $d$ as before to get
+
+\[
+\begin{array}{c}
+    k_1 + t_1k_m + u_1 \equiv 0 \mod n \\
+    k_2 + t_2k_m + u_2 \equiv 0 \mod n \\
+    \vdots \\
+    k_{m-1} + t_{m-1}k_m + u_{m-1} \equiv 0 \mod n
+\end{array}
+\]
+
+\vspace*{10px}
+
+And create the lattice $B$ as
+
+\[
+    B = 
+    \begin{pmatrix}
+     n &  \\
+     & n \\
+     & & \ddots \\
+     & & & n \\
+     t_1 & t_2 & \cdots & t_{m-1} & 1 & 0 \\
+     u_1 & u_2 & \cdots & u_{m-1} & 0 & K
+     \label{eq:lattice_ecdsa}
+    \end{pmatrix}
+\]
+
+\vspace*{10px}
+
+Same as before this lattice contains $v = (-k_1, -k_2, \ldots, k_m, K)$ and with probability TODO we can find that vector after applying LLL.
+
+\subsection{Recover $d$ knowing MSB bits from each $k$}
+
+What if we know the firsts MSB bits of each $k_i$?
+
+Well, we can write $k_i = (a_i + b_i)$, where $a_i$ is the known part and $b_i$ is the unkown part that satisfies $|b_i| < K$. If we plug these values
+into the equivalence we obtain
+
+\[
+    \begin{array}{c}
+        k_i + t_ik_m + u_i \equiv 0 \mod n \\
+        (a_i + b_i) + t_i(a_m + b_m) + u_i \equiv 0 \mod n \\
+        b_i + t_ib_m + a_i + t_ia_m + u_i \equiv 0 \mod n \\
+    \end{array}
+\]
+
+And we can set $u_i' = a_i + t_ia_m + u_i$ to be the value inside the lattice \ref{eq:lattice_ecdsa} instead of $u_i$. In this way the vector
+
+\begin{center}
+    $v = (-b_1, -b_2, \ldots, b_m, K)$
+\end{center}
+
+is in the lattice and could be found using LLL. To recover the original $(k_1, \ldots, k_m)$ we must add to $v$ the vector $w = (a_1, \ldots, a_m)$.
+
+I was able to recover the nonces with the $10$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures, but it's also possible
+to recover the nonces with less known bits as shown in \href{https://eprint.iacr.org/2020/1540}{paper}.
 

### 2021-06-03 paper.tex
Add introduction and gauss algorithm

@@
 \usepackage{wrapfig}
-\usepackage{algorithmic}
+\usepackage{algorithm}% http://ctan.org/pkg/algorithms
+%\usepackage{algorithmicx}
 \usepackage[utf8]{inputenc}
@@
 
+\chapter{Introduction}
+
+Lattices are powerful mathematical objects that can be used in computer science and mathematics to solves an extensive range of different problems.
+In the recents years many post-quantum cryptographic protocols candidates involve the use of hard lattices problems,
+for example the \textbf{Learning With Errors} \cite{LWE}.
+Lattice constructions can also be used in cryptanalysis to break cryptographic schemes, typically using reduction
+algorithms as \textbf{LLL} \cite{LLL}.
+
+To introduce the mathematics of lattices a basic linear algebra background is needed, so the second chapter is a summary of the
+basics properties needed to understand it. We used as main resource ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
+explain them, but we also tried to gives some geometrically intuition behind some operations.
+
+Cryptographic protocol as \textbf{RSA} and \textbf{ECDSA} are considered secure, however there are various attacks against a
+relaxed-model of each of them, i.e., What if we know some bits of the secret key? What if we know a part of the message before the encryption?
+We present an introduction to the attacks which involves lattices against these protocols. The code used to confirm the correctness
+of the attacks is available on the repository \cite{repo} and the main reference was
+``Recovering cryptographic keys from partial information, by example''\cite{cryptoeprint:2020:1506}.
+
 \chapter{Linear Algebra Background}
+
+We'll start with some definitions and properties needed to understand the lattices, to move later on the mathematics behind them and some
+hard problems related to it. At the end of the chapter the reader should be able to follow the math used in the other chapters.
 
@@
 \end{definition}
-A \texttt{vector space} $V$ is a subset of $\R^{m}$ which is closed under finite vector addition and scalar multiplication, with the property that
+A \textit{vector space} $V$ is a subset of $\R^{m}$ which is closed under finite vector addition and scalar multiplication, with the property that
 
@@
 
-Let $v_1,v_2,\ldots,v_k \in V$. A \texttt{linear combination} of $v_1,v_2,\ldots,v_k \in V$ is any vector of the form
+Let $v_1,v_2,\ldots,v_k \in V$. A \textit{linear combination} of $v_1,v_2,\ldots,v_k \in V$ is any vector of the form
 
@@
 
-A set of vectors $v_1,v_2,\ldots,v_k \in V$ is \texttt{linearly independent} if the the only way to get
+A set of vectors $v_1,v_2,\ldots,v_k \in V$ is \textit{linearly independent} if the the only way to get
 
@@
 
-Taken a set of linearly independent vectors $b = (v_1,\ldots,v_n) \in V$ we say that $b$ is a \texttt{basis} of $V$ if $\forall w \in V$ we can write
+Taken a set of linearly independent vectors $b = (v_1,\ldots,v_n) \in V$ we say that $b$ is a \textit{basis} of $V$ if $\forall w \in V$ we can write
 
@@
 
-The vector's length or \texttt{Euclidean norm} of $v = (x_1, x_2, \ldots, x_m)$ is
+The vector's length or \textit{Euclidean norm} of $v = (x_1, x_2, \ldots, x_m)$ is
 
@@
 
-Let $v, w \in V \subset \R^m$ and $v = (x_1, x_2, \ldots, x_m), w = (y_1, y_2, \ldots, y_m)$, the \texttt{dot product} of $v$ and $m$ is
+Let $v, w \in V \subset \R^m$ and $v = (x_1, x_2, \ldots, x_m), w = (y_1, y_2, \ldots, y_m)$, the \textit{dot product} of $v$ and $m$ is
 
@@
     \includegraphics[scale=0.2]{./img/dot_product.png}
-    \caption{Dot Product By 3Blue1Brown}
+    \caption{Dot Product By 3Blue1Brown \cite{3b1b}}
     \label{fig:dot_product}
@@
 
-An \texttt{ortoghonal basis} for a vector space $V$ is a basis $v_1, \ldots, v_m$ with the property that
+An \textit{ortoghonal basis} for a vector space $V$ is a basis $v_1, \ldots, v_m$ with the property that
 
@@
 
-If $\lVert v_i \rVert = 1$ for all $i$ then the basis is \texttt{orthonormal}.
+If $\lVert v_i \rVert = 1$ for all $i$ then the basis is \textit{orthonormal}.
 
@@
 
-Let $v_1,\ldots,v_n \in \R^m, m \ge n$ be linearly independent vectors. A \texttt{Lattice} $L$ spanned by $\{v_1,\ldots,n_n\}$ is the set of 
+Let $v_1,\ldots,v_n \in \R^m, m \ge n$ be linearly independent vectors. A \textit{Lattice} $L$ spanned by $\{v_1,\ldots,n_n\}$ is the set of 
 all integer linear combinations of $v_1,\ldots,v_n$.
@@
 If $v_i$ for every $i = 1,\ldots\,n$ has integer coordinates then the lattice is
-called \texttt{Integral Lattice}.
+called \textit{Integral Lattice}.
 
@@
 \begin{algorithm}
-    \textbf{Gauss Reduction}
+    \caption{Gauss Basis Reduction}
+    \vspace*{5px}
+    \text{Loop} \\
+    If $\lVert v_2 \rVert < \lVert v_1 \rVert$ , \text{swap }$v_1, v_2$ \\
+    m = $\left \lceil{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rceil$ \\
+    \text{If } $m = 0$, \text{return } $v_1, v_2$ \\
+    $v_2 = v_2 - mv_1$ \\
+    \text{Continue Loop}
 \end{algorithm}
@@
 
-\chapter{Cryptanlysis}
+\chapter{RSA Cryptanalysis}
 
@@
 \begin{itemize}
-    \item \textasciitilde 170 unkown bits of message from an RSA 1024-bit modulus
-    \item \textasciitilde 341 unkown bits of message from an RSA 2048-bit modulus
-    \item \textasciitilde 683 unkown bits of message from an RSA 4096-bit modulus
+    \item $\approx$ 170 unkown bits of message from an RSA 1024-bit modulus
+    \item $\approx$ 341 unkown bits of message from an RSA 2048-bit modulus
+    \item $\approx$ 683 unkown bits of message from an RSA 4096-bit modulus
 \end{itemize}
@@
 this method is better described in TODO, but the principles are the same.
+
+\subsection{Factorize modulus with known MSB bits of $p$}
+
+Knowing the most significat bits of $p$ can be used to factor the modulus $N$ ref TODO coppersmith.
+
+Let $a = 2^lb$ where $b$ are the bits known of $p$, then $p = a + r$ for some small value of $r$.
+
+Using as lattice basis
+
+\[
+    B = 
+    \begin{pmatrix}
+        X^2 & Xa & 0 \\
+        0 & X & a \\
+        0 & 0 & N
+    \end{pmatrix} 
+\]
+
+And applying LLL we can find $r$.
+
+\chapter{ECDSA Cryptanalysis}
 
@@
 
-\subsection{Recover $d$ from many signatures}
+\subsection{Recover $d$ from many signatures with small $k_i$}
 
@@
 
-\subsection{Recover $d$ knowing MSB bits from each $k$}
+\subsection{Recover $d$ knowing MSB bits of each $k_i$}
 

### 2021-06-03 paper.tex
Add gram-schmidt and gauss reduction algorithm2e

@@
 \usepackage{wrapfig}
-\usepackage{algorithm}% http://ctan.org/pkg/algorithms
-%\usepackage{algorithmicx}
+% \usepackage{algorithm}% http://ctan.org/pkg/algorithms
+% \usepackage[ruled,vlined]{algorithm2e}
+% \usepackage{algorithm}
+\usepackage[]{algorithm2e}
+\usepackage{algorithmic}
 \usepackage[utf8]{inputenc}
@@
 
-\begin{algorithm}
-    \textbf{Gram-Schmidt Algorithm}
+\begin{algorithm}[H]
+    \vspace*{5px}
+    $v_1^* = v1$\;
+    \\
+    \For{$i \gets 2$ \KwTo $n$}{
+        $\mu_{ij} = v_i \cdot v_j^* / \lVert v_j^* \rVert ^ 2$ for $1 \le j < i$ \;
+        \\
+        $v_i^* = v_i - \sum_{j=1}^{i-1} \mu_{ij}v_j^*$ \;
+    }
+    \caption{Gram-Schmidt Algorithm}
 \end{algorithm}
@@
 
+\clearpage
+
 \section{Problems}
@@
 
-\begin{algorithm}
-    \caption{Gauss Basis Reduction}
-    \vspace*{5px}
-    \text{Loop} \\
-    If $\lVert v_2 \rVert < \lVert v_1 \rVert$ , \text{swap }$v_1, v_2$ \\
-    m = $\left \lceil{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rceil$ \\
-    \text{If } $m = 0$, \text{return } $v_1, v_2$ \\
-    $v_2 = v_2 - mv_1$ \\
-    \text{Continue Loop}
-\end{algorithm}
-
-\begin{figure}[b]
+\begin{figure}[!b]
     \centering
@@
 
+\begin{algorithm}[H]
+    \vspace*{5px}
+    \While{true}{
+        \If{$\lVert v_2 \rVert < \lVert v_1 \rVert$}{
+            swap $v_1, v_2$ \;
+        }
+        m = $\left \lfloor{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rfloor$ \\
+        \If{$m = 0$}{
+            return $v_1, v_2$ \;
+        }
+        $v_2 = v_2 - mv_1$ \\
+    }
+    \caption{Gauss Basis Reduction}
+\end{algorithm}
+
 If we take for example $v_1 = (8, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
@@
 
-However the bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to find such vector.
+The bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to find such vector.
 

### 2021-06-03 paper.tex
Add algorithm LLL and references

@@
     \caption{Gram-Schmidt Algorithm}
+    \label{alg:gram_schmidt}
 \end{algorithm}
@@
 
-TODO: Write algorithm and explain some steps
+\begin{algorithm}[H]
+    \vspace*{5px}
+    Input basis ${v_1, \ldots, v_n}$ \; \\
+    $k = 2$ \; \\
+    $v_1* = v_1$ \; \\
+    \While{$k \le n$}{
+        \For{$j = k -1$ \KwTo $1$ step $-1$} {
+            $v_k = v_k - \left\lfloor\mu_{k, j}\right\rceil \boldsymbol{v}_{j}$  [size-reduction] \;
+        }
+        \eIf{$\lVert v_k^* \rVert^2 \ge (\frac{3}{4} - \mu_{k, k-1}^2) \lVert v_{k-1}^2 \rVert$}{
+            $k = k + 1$ \;  [Lovàsz-condition]
+        }{
+            Swap $v_{k-1}$ and $v_k$ [swap-step] \; \\
+            $k = \max(k - 1, 2)$
+        }
+    }
+    Note: At each step, $v_1^*, \ldots, v_k^*$ is the orthogonalized set of vectors
+    obtained with the Gram-Schmidt \ref{alg:gram_schmidt}. \\
+    \vspace*{5px}
+    $\mu_{i,j}$ is the quantity $(v_i \cdots v_j^*) / \lVert v_j^* \rVert^2$. \\
+    Output reduced basis ${v_1, \ldots, v_n}$
+    \caption{LLL reduction algorithm}
+\end{algorithm}
+
+The running time of the algorithm is polynomial and executes the main loop no more than
+$\mathcal{O}(n^2\log n + n^2\log M)$ steps, where $M = max \lVert v_i \rVert$. \\
+
+Kelby Ludwig explains an intuition behind every steps of the algorithm \cite{lllintuition}, and Oded Regev
+gives a more rigorous explanation of the algorithm and the properties \cite{lllexplanation}.
 

### 2021-06-03 paper.tex
Update SVP and CVP

@@
 
-\title{Introduction to LLL\\``Cryptography''}
+\title{Introduction to Lattices Attacks\\``Cryptography''}
 
@@
 
-\textbf{The Shortest Vector Problem} (\texttt{SVP}): Find a nonzero vector $v \in L$ that minimez the Euclidean norm $\lVert v \rVert$.
+\textbf{The Shortest Vector Problem} (\texttt{SVP}): \textit{Find a nonzero vector $v \in L$ that minimez the Euclidean norm $\lVert v \rVert$.}
+
+Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
+gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.
 
@@
     \centering
-    \includegraphics[width=0.5\textwidth]{./img/gauss_svp.png}
+    \includegraphics[width=0.6\textwidth]{./img/gauss_svp.png}
     \caption{Gauss reduction}
@@
 \end{figure}
-
-Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
-gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.
 
@@
 
-If we take for example $v_1 = (8, 4), v_2 = (7, 5)$ and apply the gauss reduction algorithm we
-obtain $w_1 = (1, -1), w_2 = (6, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$ spanned by $v_1, v_2$.
+\textbf{Example}. Let $L$ a lattice spanned by $v_1 = (8, 4), v_2 = (7, 5)$, if we apply the gauss reduction algorithm we
+obtain $w_1 = (1, -1), w_2 = (6, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$.
 
-The bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to find such vector.
+The bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to solve it.
 
@@
 
-\textbf{The Closest Vector Problem} (\texttt{CVP}): Given a vector $w \in \R^m$ that is not in $L$, find a vector $v \in L$ that is closest to $w$,
-in other words find a vector $v \in L$ that minimizes the Euclidean norm $\lVert w - v \rVert$.
+\textbf{The Closest Vector Problem} (\texttt{CVP}): \textit{Given a vector $t \in \R^m$ that is not in $L$, find the vector $v \in L$
+    closest to $t$, in other words find a vector $v \in L$ that minimizes the Euclidean norm $\lVert t - v \rVert$.}
 
-TODO FIX \ref{fig:cvp} is wrong, the lattice is different.
-
-\begin{figure}[t]
+\begin{figure}[!ht]
     \centering
-    \includegraphics[width=0.5\textwidth]{./img/cvp.png}
+    \includegraphics[width=0.6\textwidth]{./img/cvp.png}
     \caption{CVP}
@@
 
-TODO: CVP and SVP are related.
+\texbtf{Example}. Let $L$ a lattice spanned by $v_1 = (0, 1), v_2 = (2, 0)$, and a target vector $t = (2.3, 2.4)$. The closest vector
+to $t$ in the lattice $L$ is $w = (2, 2)$.\\
 
-% matrix([[0, 0, 1], [1, 1, 2], [1, 2, 1]])
+Both \textbf{CVP} and \textbf{SVP} are $\mathcal{NP}$-hard problems, thus the complexity of the problem increments with the dimension
+of the lattice. They can be used as primitive to create a trapdoor functions for a cryptographic scheme.
+
+There are various algorithms that can output a solution under certain constraints for an approximation of both \textbf{SVP}
+and \textbf{CVP}, for example \textbf{LLL}\cite{LLL} and \textbf{Babai's algorithm}\cite{babai} respectively.
+
 \chapter{LLL}

### 2021-06-03 paper.tex
Determinant definition

@@
 basics properties needed to understand it. We used as main resource ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
-explain them, but we also tried to gives some geometrically intuition behind some operations.
+explain them, but we also tried to gives some geometrical intuition behind some operations.
 
@@
 If we take $v_1=(4, 1), v_2=(2, 3)$ as basis and apply gram schmidt we obtain $u_1=v_1=(4, 1), u_2=(-10/17, 40/17)$ as shown in \ref{fig:gram_schmidt}
+
+\begin{definition}
+    \textbf{Determinant}
+\end{definition}
+
+The \textit{determinant} of a square matrix is a function that satisfies the following properties:
+
+\begin{enumerate}
+    \item The determinant is linear in each row.
+    \item The determinant reverses sign if two rows are interchanged.
+    \item The determinant of the identity matrix is equal to 1.
+\end{enumerate}
+
+If the determinant of a matrix is $0$ then the matrix is called \textbf{singular} (without an inverse).\\
+
+Grant Sanderson created fantastic animations to understand the geometrical intuition behind the \textit{determinant}\cite{determinant}.
 

### 2021-06-03 paper.tex
Add references RSA

@@
 \begin{definition}
-    \textbf{Lineaer Independece}
+    \textbf{Linear Independece}
 \end{definition}
@@
 
-The \textbf{Lenstra-Lenstra-Lovász} \textit{LLL} or \textit{$L^3$} is a polynomial time algorithm to find a "shorter" basis.
+The \textbf{Lenstra-Lenstra-Lovász} \textit{LLL}\cite{LLL} or \textit{$L^3$} is a polynomial time algorithm to find a ``short'' basis of a lattice.
 
@@
     \item Factoring polynomials over the integers. For example, given $x^2 - 1$ factor it into $x + 1$ and $x - 1$.
-    \item Integer Programming. This is a well-known \textbf{NP}-complete problem. Using LLL, one can obtain a polynomial time solution
+    \item Integer Programming. This is a well-known $\mathcal{NP}$-complete problem. Using \textbf{LLL}, one can obtain a polynomial time solution
           to integer programming with a fixed number of variables.
     \item Approximation to the \textbf{CVP} or \textbf{SVP}, as well as other lattice problems.
-    \item Application in cryptanalysis.
+    \item Cryptanalysis (break cryptographic protocols).
 \end{enumerate}
@@
 \chapter{RSA Cryptanalysis}
-
-% \section{Attack Knapsack}
 
@@
     \item If $q = p + x$ where $x$ is small enough than it's easy to recover the factors of $N$ computing $A = \sqrt{N}$ and compute
-            $p = A - x$ for different value of $x$ until $N \mod p = 0$, then we have found $q = N / p$
-    \item Many more attacks can be found TODO.
+            $p = A - x$ for different value of $x$ until $N \mod p = 0$, then we have found $q = N / p$.
+    \item If $d$ is too small (for example to accelerate decryption) then Wiener found a way to recover the private key $d$ \cite{wiener}.
+    \item Other attacks can be found on the excellent survey by Dan Boneh \cite{boneh99twentyyears}.
 \end{itemize}
@@
 
-We want to attack a relaxed model of RSA where we know a part of the message $m$.
-We start introducing the \ref{TODO} coppersmith attack and the math behind it.
+We start introducing the main ideas of Coppersmith's attack \cite{coppersmith96} and the math behind it.
+The attack can be used against \textbf{RSA} when a small $e$ is used. In 2017 the attack was used to exploit
+\href{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-15361}{CVE-2017-15361} also named \textbf{ROCA}
+(Return Of Coppersmith's Attack) \cite{roca}.
 
@@
 
-\subsection{Example}
+\subsection{Recover plaintext with known MSB bits of $m$}
 
-We have a 100-bit \textbf{RSA} modulus
+We will use a simplified version of the Coppersmith's attack that works when the root is approximately less than $N^{\frac{1}{6}}$.
+
+\textbf{Problem setup}. Let $N$ be an \textbf{RSA} modulus of $97$-bit:
 
 \begin{center}
-    $N=0xf046522fb555a90bdc558fc93$ and $e = 3$.
+    $N=\texttt{0x1a34992f64135aedaa0fe2bfd}$ and $e = 3$.
 \end{center}
@@
 \[
-    z = pad || m = 0x74686973206b65793a || m
+    z = pad || m = \texttt{0xffffffffffffffffffffff} || m
 \]
 
-where $||$ is the concatenation. The padding is the ascii encoding of ``this key:''\\
+where $||$ is the concatenation.
 
@@
 \[
-    c = z^e \mod N = 0x5b603cda4b72100c6f25954fc
+    c = z^e \mod N = \texttt{0x11701d5479bcdef207cba6937}
 \]
@@
 Suppose that we don't know the factorization of $N$ and we would like to know the message $m$.
-However we know the padding and that the length of $m < 2^{16}$.
+We know the padding and that the message $m$ is 2 bytes long, composed by only ascii letters, so $m < \texttt{0x7b7b}$.
 
@@
 \[
-a = 0x74686973206b65793a0000
+    a = \texttt{0xffffffffffffffffffffff0000}
 .\]
@@
 \begin{align*}
-    f(x) = x^3 + 0x15d393c596142306bae0000x^2 + 0x1b53c5e184a49b39f9ad9eedbx\\
-    + 0x486a5d936fb568185c8ff0506
+    f(x) = x^3 + \texttt{0x17d7f55d0c9dc5851af54957c}x^2 + \texttt{0x3cf96fed2ea927527a2ed329}x\\
+    + \texttt{0x32882e547964b3bcf75d315e}
 \end{align*}
@@
 \textbf{Lattice contruction}. Let the coefficients of $f$ be $f(x) = x^3 + f_2x^2 + f_1x + f_0$
-and $X = 2^{16}$ be the upper bound of the size of the root $m$. We can construct the matrix
+and $X = \texttt{0x7b7b}$ be the upper bound of the size of the root $m$. We can construct the matrix
 
@@
     \begin{split}
-    v = (0x90843131bc53X^3 + 0x2736f60b1c7ba3294X^2, \\
-    -0x1bec331b20625341b6d73X, 0x47336b98335c143ac912ec9e)
+    v = (-\texttt{0xd55d67baf71d}X^3, \texttt{0x3cf3cca3200a58bf}X^2, \\
+    \texttt{0x3854d44211e80f248449}X, -\texttt{0xec93bf51cf766f7b9f1e5e6})
     \end{split}
@@
     \begin{split}
-        g(x) = 0x90843131bc53x^3 + 0x2736f60b1c7ba3294x^2 \\
-        -0x1bec331b20625341b6d73x + 0x47336b98335c143ac912ec9e
+        g(x) = -\texttt{0xd55d67baf71d}x^3 +  \texttt{0x3cf3cca3200a58bf}x^2 \\
+        \texttt{0x3854d44211e80f248449}x -\texttt{0xec93bf51cf766f7b9f1e5e6}
     \end{split}
@@
 
-We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solves for $X$ this will be satisfied when $X < (\frac{N}{16})^{\frac{1}{6}}$.
+We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solves for $X$ this will be satisfied when
+$X < (\frac{N}{16})^{\frac{1}{6}}$. We can consider the $\sqrt{4}$ an error term to have $X < N^{\frac{1}{6}}$.
 With the numbers we have this inequality is verified, however even if the bound of the shortest vector is larger we still have some possibilities to
@@
 
-If we compute the root of $g(x)$ over the integers we obtain $m = 0x6162$ which is the correct result.\\
+If we compute the root of $g(x)$ over the integers we obtain $m = \texttt{0x4142} = $ ``AB'' which is the correct result.\\
 
@@
 To compute bigger root a bigger lattice with more polynomials generated with \ref{eq:create_pol} is needed,
-this method is better described in TODO, but the principles are the same.
+this method is better described in \cite{may2011} and a detailed implementation in sagemath by David Wong is available \cite{wong2015}.
 

### 2021-06-04 paper.tex
ROCA explanation

@@
 
-\section{Problems}
+\section{Lattice Problems}
 
@@
 We start introducing the main ideas of Coppersmith's attack \cite{coppersmith96} and the math behind it.
-The attack can be used against \textbf{RSA} when a small $e$ is used. In 2017 the attack was used to exploit
+The attack can be used against \textbf{RSA} when a small $e$ is used, but also
+to factorize the modulus. In 2017 the attack was used to exploit
 \href{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-15361}{CVE-2017-15361} also named \textbf{ROCA}
@@
 B = 
+\label{mat:lattice_rsa}
 \begin{pmatrix}
@@
 We applied Howgrave-Graham with $m=1$ (the $N^m$ parameter not the message).\\
-With this lattice construction every vector is of the form $v = (v_1X^3, v_2X^2, v_1X, v_0)$, because any
+With this lattice construction every vector is of the form $v = (v_3X^3, v_2X^2, v_1X, v_0)$, because any
 integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=0,..,\dim(B)-1$.
@@
 
-Knowing the most significat bits of $p$ can be used to factor the modulus $N$ ref TODO coppersmith.
+Lattices can also be used to factor a modulus $N$ knowing the most significant bits of one of the factor.
+Let $a = 2^lb$ where $b$ are the bits known of $p$, then $p = a + r$ for some small value of $r$.
+We can rewrite the problem to find the root $r$ of $f(x) = a + x \mod p$ such that $f(r) = p \equiv 0 \mod p$.
+Suppose that we know the bound of $r$ such that $|r| < X$ for some bound $X$.
 
-Let $a = 2^lb$ where $b$ are the bits known of $p$, then $p = a + r$ for some small value of $r$.
-
-Using as lattice basis
+We can construct the following lattices
 
@@
 
-And applying LLL we can find $r$.
+\vspace*{10px}
+
+Notice that the rows correspond to the polynomials $x(x + a)$, $(x + a)$, $N$ and that each of these polynomials will
+be $0 \mod p$ when $x = r$. As before \ref{mat:lattice_rsa}, every polynomial is scaled by $X$ which is the upperbound.
+
+We need to verify that the shortest vector that we can with \textbf{LLL} will be less than $p$ because if $g(x) < p$,
+then by construction we can compute $g(r) = 0$ over the integers.
+In this case we have
+
+\[
+    (detB)^{\frac{1}{\dim L}} = (X^3N)^{\frac{1}{3}} < p
+\]
+
+Solving for $X$ we obtain $X < p^{\frac{1}{3}}$, so this method works for every $|r| < p^{\frac{1}{3}}$.
+
+To find $r$ we just need to apply \textbf{LLL} and take the first vector (shortest) that will be of the form $v = (v_2X^2, v_1X, v_0)$.
+
+The last step is to construct $g(x) = v_2x^2 + v_1x + v_0$ (just divides every coefficient by $X^i$)
+and computes the roots over the integers to find $r$. We implemented the attack against a modulus
+of \texbtf{RSA}-$1024$ knowing the $160$ most significant bits of $p$. The attack can be expanded
+until $X < p^{\frac{1}{2}}$ with a bigger lattice.
+
+\subsection{Real World case study: ROCA}
+
+\textbf{ROCA}\cite{roca} is a vulnerability discovered in the 2017 in a software library \textit{RSALib} in the generation
+of the public modulus for \textbf{RSA}. The attack is believed to affects millions of smart cards. The vulnerbality
+resides in the generation of prime numbers, since embedded devices don't have lots of computational resources a fast way
+was needed. Every prime generated has the following structure:
+
+\[
+    p = kM + (g^a \mod M)
+    \label{eq:roca}
+\]
+
+Where $k, a$ are random values different for every prime (unkown), $g = 65537$ and $M$ is known and it's a \textit{primorial} number.
+A \textit{primorial} number $M$ is the product of the the first $n$ successive primes
+
+\[
+    M = P_n# = \prod_{i=1}^{n} P_i
+\]
+
+where $n$ is related to key size. In the case of \textit{RSALib} the primorial number used had similar dimension to $p$,
+and the value $a, k$ didn't have much entropy. The modulus is
+
+\[
+    N = (kM + g^{a}\mod M)(lM + g^{b}\mod M)
+\]
+
+for $a, b, k, l \in \Z$. It's equivalent to
+
+\[
+    N \equiv g^{a + b} \equiv g^{c} \mod M
+\]
+
+for some $c \in \Z$ since all the multiples of $kM$ or $lM$ are $0 \mod M$.
+
+It's possible to compute the discrete logarithm of $g^c \mod M$ since the size of $|M|$ is smooth with
+Pohlig-Hellman algorithm \cite{pohlig}. With $c$ we can set a bound to the value of $a$ since
+
+\[
+    \frac{c}{2} \le a \le \frac{c + ord}{2}
+\]
+
+where $ord$ is the multiplicative order of the generator $g \in Z_M$.
+
+Once we know the bound of $a$ we can try to find the value of $k$ with the Coppersmith's method \cite{coppersmith96} for every possible $a$.
+
+The concept of the algorithm is the following:
+
+\begin{algorithm}[H]
+    \vspace*{5px}
+    \textbf{Input: } $N, M, g, ord, X$ \; \\
+    $c = \log_{g}N \mod M$ \;\\
+    \For{$a \gets (\frac{c}{2}, \frac{c + ord}{2})$}{
+        \vspace*{5px}
+        $f(x) = xM + (g^a \mod M)$ \; \\
+        $g(x) = \frac{1}{M}f(x)$ [make monic, the roots are the same] \; \\
+        $k = $ coppersmith($g(x), N, X$) [find k] \; \\ 
+        $p = kM + (g^a \mod M)$  [candidate] \; \\
+        \If{$N \mod p = 0$}{
+            return $p$ \;
+        }
+    }
+\end{algorithm}
+
+In practice however the bound of $a$ is too big, so the authors found a way the problem to a smaller $M'$ since the
+bitsize of $M$ are more than sufficient for making the attack works with Coppersmith's algorithm. Their optimization
+find a new $M'$ such that
+
+\begin{itemize}
+    \item $(p, q)$ are still of the form \ref{eq:roca}, so $M'$ must be a divisor of $M$.
+    \item Coppersmith's algorithm will find $k'$ for the correct guess of $a'$.
+    \item Find a small order of $g \in \Z_M'$ to make $a'$ smaller.
+\end{itemize}
+
+We were able to reproduce the attack in sagemath against \textbf{RSA}-512, and we used as $M'$ the value
+that Bruno Produit \cite{rocaopt} made available in his thesis and David Wong's implementation of Coppersmith's attack \cite{wong2015}.
 

### 2021-06-04 paper.tex
Add references for ECDSA attacks

@@
 
-\title{Introduction to Lattices Attacks\\``Cryptography''}
+\title{Introduction to Lattice-based Attacks\\``Cryptography''}
 
@@
 Kelby Ludwig explains an intuition behind every steps of the algorithm \cite{lllintuition}, and Oded Regev
-gives a more rigorous explanation of the algorithm and the properties \cite{lllexplanation}.
+gives a more rigorous explanation of the algorithm and the properties \cite{lllexplanation}.\\
 
-\section{Applications}
-
-There are many applications of LLL
+Some of the applications of the algorithm are the following:
 
@@
             $p = A - x$ for different value of $x$ until $N \mod p = 0$, then we have found $q = N / p$.
-    \item If $d$ is too small (for example to accelerate decryption) then Wiener found a way to recover the private key $d$ \cite{wiener}.
+    \item It's possible to recover $d$ if it is too small (for example to accelerate decryption) using the Wiener's attack \cite{wiener}.
     \item Other attacks can be found on the excellent survey by Dan Boneh \cite{boneh99twentyyears}.
@@
 The attack can be used against \textbf{RSA} when a small $e$ is used, but also
-to factorize the modulus. In 2017 the attack was used to exploit
+to factorize the modulus if some bits of $p$ or $q$ are known. In 2017 the attack was used to exploit
 \href{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-15361}{CVE-2017-15361} also named \textbf{ROCA}
@@
 
-\subsection{Real World case study: ROCA}
+\subsection{Real world case study: ROCA}
 
-\textbf{ROCA}\cite{roca} is a vulnerability discovered in the 2017 in a software library \textit{RSALib} in the generation
+\textbf{ROCA}\cite{roca} is a vulnerability discovered in 2017 in a software library \textit{RSALib} in the generation
 of the public modulus for \textbf{RSA}. The attack is believed to affects millions of smart cards. The vulnerbality
@@
 
-Where $k, a$ are random values different for every prime (unkown), $g = 65537$ and $M$ is known and it's a \textit{primorial} number.
+Where $k, a$ are random values different for every prime (unkown), $g = 65537$ and $M$ it's a \textit{primorial} number.
 A \textit{primorial} number $M$ is the product of the the first $n$ successive primes
@@
 It's possible to compute the discrete logarithm of $g^c \mod M$ since the size of $|M|$ is smooth with
-Pohlig-Hellman algorithm \cite{pohlig}. With $c$ we can set a bound to the value of $a$ since
+Pohlig-Hellman algorithm \cite{pohlig}. With $c$ we can set the bound to the value of $a$ since
 
@@
     }
+    \caption{Exploit idea}
 \end{algorithm}
 
-In practice however the bound of $a$ is too big, so the authors found a way the problem to a smaller $M'$ since the
+In practice however the bound of $a$ is too big, so the authors found a way to move the same problem to a smaller $M'$ since the
 bitsize of $M$ are more than sufficient for making the attack works with Coppersmith's algorithm. Their optimization
@@
 
-We were able to reproduce the attack in sagemath against \textbf{RSA}-512, and we used as $M'$ the value
+We were able to reproduce the attack in sagemath against \textbf{RSA}-$512$, and we used as $M'$ the value
 that Bruno Produit \cite{rocaopt} made available in his thesis and David Wong's implementation of Coppersmith's attack \cite{wong2015}.
@@
 \textbf{ECDSA} is a variant of the Digital Signature Algorithm (\textbf{DSA}) which uses elliptic curve cryptography.
-To digitally sign a message we have 3 public parameters
+There are 3 public parameters:
 
@@
 
-We also need to create a private key $d \in [1, n-1]$ and public key $Q = dG$. To digitally \textbf{sign} a message $m$:
+We also need to create a private key $d \in [1, n-1]$ and public key $Q = dG$. To \textbf{sign} a message $m$:
 
 \begin{enumerate}
-    \item Compute $h = $ HASH$(m)$ where HASH is a cryptographic hash functions.
-    \item Select a random integer $k \in [1, n-1]$.
-    \item Calculate $P = kG = (x_1, y_1)$ and set $r = (x_1)$.
+    \item Compute $h = $ MSB(HASH$(m))$ where HASH is a cryptographic hash function, for example SHA-256, and MSB take the $n$ most significant bits.
+    \item Select a random integer $k \in [1, n-1]$ (nonce).
+    \item Calculate $P = kG = (x_1, y_1)$ and set $r = (x_1)$ if $x_1 \neq 0$, otherwise repeat the steps.
     \item Compute $s = k^{-1}(h + dr) \mod n$, if $s = 0$ repeat the steps.
@@
     \item It's possible to recover $d$ if the parameter $k$ is not generated with a cryptographically secure pseudo random generator.
-    \item If the elliptic curve used is not standardized (custom) then it's possible that the discrete logarithm is easily solvable.
+    \item If the elliptic curve used is not standardized (custom) then it's possible that the discrete logarithm is easily solvable
+        \cite{giuliani99attackson}, \cite{mov} \cite{smartass}.
 \end{itemize}
@@
 
+The lattice-based attacks presented here are based on the \textit{Hidden Number Problem} introduced
+by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significan bits
+of $k$ can potentially leak the entire nonce \cite{ecdsa_nonce}.
+
 \subsection{Recover $d$ from a pair of signatures with small $k_1, k_2$}
 
+\textbf{Problem setup}.
 Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
@@
 
-Same as before this lattice contains $v = (-k_1, -k_2, \ldots, k_m, K)$ and with probability TODO we can find that vector after applying LLL.
+Same as before this lattice contains $v = (-k_1, -k_2, \ldots, k_m, K)$ that can be found using LLL.
 
@@
 
-I was able to recover the nonces with the $10$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures, but it's also possible
-to recover the nonces with less known bits as shown in \href{https://eprint.iacr.org/2020/1540}{paper}.
+Without any optimization we were able to recover the nonces with the $10$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures,
+but it's also possible to recover the nonces with less known bits as shown in the results obtained by Albrecht and Heninger \cite{ecdsa_result}.
 

### 2021-06-07 lattice_based_attacks.tex
Rename repository and paper
Update conclusions

--- 2021-06-04 paper.tex
@@
 
-\vspace*{10px}
+\clearpage
 
@@
 
-The lattice-based attacks presented here are based on the \textit{Hidden Number Problem} introduced
+The lattice-based attacks presented here are based on the \textit{HNP (Hidden Number Problem)} introduced
 by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significan bits
 of $k$ can potentially leak the entire nonce \cite{ecdsa_nonce}.
+In 2020 a group of researcher were able to leak the MSBs of \textit{DH} and \textit{DHE} secrets in \textbf{TLS $\le$ 1.2}
+and using a similar lattice constructions as the one we will describe to solve the \textit{HNP}
+and thus breaks the protocol \cite{cryptoeprint:2020:1151} (Raccoon Attack).
 
@@
 Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
-$G = (\texttt{0xcc3b3d1a0c4938ef}, \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.
+$G = (\texttt{0xcc3b3d1a0c4938ef}, \\ \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.
 
-\vspace*{10px}
+\clearpage
 
@@
 
-Without any optimization we were able to recover the nonces with the $10$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures,
-but it's also possible to recover the nonces with less known bits as shown in the results obtained by Albrecht and Heninger \cite{ecdsa_result}.
+Without any optimization we were able to recover the nonces with the $8$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures 
+and with a probability bigger than $50\%$ with $7$ MSB bits known.
+
+It's possible to optimize the attack to recover the nonces with less known bits as shown in the results obtained by
+Albrecht and Heninger \cite{ecdsa_result}.
 
@@
 
-$gg^2$
+The results obtained from the implementation of the attacks are satisfactory and can be used against real world practical cases.
+There is a fair amount of probability and heuristic to make the attacks works that isn't discussed in detail.
+As with other branch of mathematics not all theorems and properties are proved to be useful the moment they were first introduced
+but can become useful years later as the hidden number problem that become crucial for the Raccoon Attack.
+The study on how to exploit side-channel attacks (ex. knowing some bits of $p$ in \textbf{RSA}) has been proven useful
+with \textbf{ROCA}.
+The most used cryptographic protocol used has been proved secure but it's very easy to implement them wrong and side-channel
+vulnerabilities can heavily compromise the security of the protocol.
 
 \bibliographystyle{plain}
-\bibliography{paper}
+
+\bibliography{lattice_based_attacks}
 

### 2021-06-07 lattice_based_attacks.tex
Fix grammars

@@
 % \usepackage{algorithm}% http://ctan.org/pkg/algorithms
-% \usepackage[ruled,vlined]{algorithm2e}
+% \usepackage[ruled, vlined]{algorithm2e}
 % \usepackage{algorithm}
@@
 \usepackage{fontenc}
-\usepackage{amsmath,stmaryrd,mathtools,algorithm}
+\usepackage{amsmath, stmaryrd, mathtools, algorithm}
 \usepackage{amssymb}
@@
 basics properties needed to understand it. We used as main resource ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
-explain them, but we also tried to gives some geometrical intuition behind some operations.
+explain them, but we also tried to give some geometrical intuition behind some operations.
 
@@
 
-Let $v_1,v_2,\ldots,v_k \in V$. A \textit{linear combination} of $v_1,v_2,\ldots,v_k \in V$ is any vector of the form
+Let $v_1,v_2,\ldots,v_k \in V$. A \textit{linear combination} of $v_1,v_2,\ldots,v_k \in V$ is any vector of the form:
 
@@
 
-\begin{figure}[!tbp]
+\begin{figure}[!bp]
     \begin{minipage}[b]{0.50\textwidth}
@@
 
-\texbtf{Example}. Let $L$ a lattice spanned by $v_1 = (0, 1), v_2 = (2, 0)$, and a target vector $t = (2.3, 2.4)$. The closest vector
+\textbf{Example}. Let $L$ a lattice spanned by $v_1 = (0, 1), v_2 = (2, 0)$, and a target vector $t = (2.3, 2.4)$. The closest vector
 to $t$ in the lattice $L$ is $w = (2, 2)$.\\
@@
 
-Kelby Ludwig explains an intuition behind every steps of the algorithm \cite{lllintuition}, and Oded Regev
+Kelby Ludwig explains an intuition behind every step of the algorithm \cite{lllintuition}, and Oded Regev
 gives a more rigorous explanation of the algorithm and the properties \cite{lllexplanation}.\\
 
-Some of the applications of the algorithm are the following:
+Some applications of the algorithm are the following:
 
@@
     \item Fix $e = 65537$ or $e = 3$ (public).
-    \item Find two primes $p, q$ such that $p - 1$ and $q - 1$ are relatively prime to $e$, i.e. gcd$(e, p-1) = 1$ and gcd$(e, q-1) = 1$.
+    \item Find two primes $p, q$ such that $p - 1$ and $q - 1$ are relatively prime to $e$, gcd$(e, p-1) = 1$ and gcd$(e, q-1) = 1$.
     \item Compute $N = p * q$ and $\phi(n) = (p-1) * (q-1)$
@@
 
-RSA relies on the hardness of factoring the modulo $N$ and we don't have a polynomial algorithm to factor it, so it's considered secure.
-However there are different attacks against textbook RSA or bad implementations:
+RSA relies on the hardness of factoring the modulo $N$, and we don't have a polynomial algorithm to factor it, so it's considered secure.
+However, there are different attacks against textbook RSA or bad implementations:
 
@@
             $p = A - x$ for different value of $x$ until $N \mod p = 0$, then we have found $q = N / p$.
-    \item It's possible to recover $d$ if it is too small (for example to accelerate decryption) using the Wiener's attack \cite{wiener}.
+    \item It's possible to recover $d$ if it is too small (in practice could be used to accelerate decryption) using the Wiener's attack \cite{wiener}.
     \item Other attacks can be found on the excellent survey by Dan Boneh \cite{boneh99twentyyears}.
@@
 
-Suppose $N$ is an \textbf{RSA} modulus and we don't know the factorization of it. Let's have an univariate integer polynomial $f(x)$ with degree $n$
+Suppose $N$ is an \textbf{RSA} modulus, and we don't know the factorization of it. Let's have an univariate integer polynomial $f(x)$ with degree $n$
 
@@
 using the following theorem
+
+\clearpage
 
@@
         modulo $N^m$.
-    \item If we craft the lattice properly, the norm of shortest vector on the reduced basis will satisfy \ref{eq:pol}.
+    \item If we craft the lattice properly, the norm of the shortest vector on the reduced basis will satisfy \ref{eq:pol}.
         We know the length's bound of the shortest vector that LLL could find.
@@
 
-Suppose that we don't know the factorization of $N$ and we would like to know the message $m$.
+Suppose that we don't know the factorization of $N$, and we would like to know the message $m$.
 We know the padding and that the message $m$ is 2 bytes long, composed by only ascii letters, so $m < \texttt{0x7b7b}$.
@@
 
-Thus we have that $c = (a + m)^3 \mod N$, for an unkown small $m$.
-We can define $f(x) = (a + x)^3 - c$, and so we setup the problem to find a small root $m$ such that $f(m) \equiv 0 \mod N$
+Thus, we have that $c = (a + m)^3 \mod N$, for an unkown small $m$.
+We can define $f(x) = (a + x)^3 - c$, and setup the problem to find a small root $m$ such that $f(m) \equiv 0 \mod N$
 
@@
 The rows of the matrix correspond to the coefficient vectors of the polynomials $f(x), Nx^2, Nx$ and $N$, furthermore we know
-that each polynomials will be 0 modulo $N$ if evaluated at $x = m$.
+that each polynomial will be 0 modulo $N$ if evaluated at $x = m$.
 We applied Howgrave-Graham with $m=1$ (the $N^m$ parameter not the message).\\
 With this lattice construction every vector is of the form $v = (v_3X^3, v_2X^2, v_1X, v_0)$, because any
-integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=0,..,\dim(B)-1$.
+integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=\dim(B)-1,..,0$.
 
@@
 
-We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solves for $X$ this will be satisfied when
+We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solve for $X$ this will be satisfied when
 $X < (\frac{N}{16})^{\frac{1}{6}}$. We can consider the $\sqrt{4}$ an error term to have $X < N^{\frac{1}{6}}$.
@@
 
-If we compute the root of $g(x)$ over the integers we obtain $m = \texttt{0x4142} = $ ``AB'' which is the correct result.\\
+Computing the root of $g(x)$ over the integers we obtain $m = \texttt{0x4142} = $ ``AB'' which is the correct result.\\
 
@@
 
-We need to verify that the shortest vector that we can with \textbf{LLL} will be less than $p$ because if $g(x) < p$,
+We need to verify that the shortest vector that we can find with \textbf{LLL} will be less than $p$ because if $g(x) < p$,
 then by construction we can compute $g(r) = 0$ over the integers.
@@
 and computes the roots over the integers to find $r$. We implemented the attack against a modulus
-of \texbtf{RSA}-$1024$ knowing the $160$ most significant bits of $p$. The attack can be expanded
+of \textbf{RSA}-$1024$ knowing the $160$ most significant bits of $p$. The attack can be expanded
 until $X < p^{\frac{1}{2}}$ with a bigger lattice.
@@
 \textbf{ROCA}\cite{roca} is a vulnerability discovered in 2017 in a software library \textit{RSALib} in the generation
-of the public modulus for \textbf{RSA}. The attack is believed to affects millions of smart cards. The vulnerbality
+of the public modulus for \textbf{RSA}. The attack is believed to affect millions of smart cards. The vulnerbality
 resides in the generation of prime numbers, since embedded devices don't have lots of computational resources a fast way
@@
 Where $k, a$ are random values different for every prime (unkown), $g = 65537$ and $M$ it's a \textit{primorial} number.
-A \textit{primorial} number $M$ is the product of the the first $n$ successive primes
-
-\[
-    M = P_n# = \prod_{i=1}^{n} P_i
+A \textit{primorial} number $M$ is the product of the first $n$ successive primes
+
+\[
+    M = P_n\# = \prod_{i=1}^{n} P_i
 \]
@@
 Given the points $Q, G$ such that $Q = k*G$ it's considered an hard problem to find $k$.
-However as RSA there are lots of implementation attacks
+However, as RSA, there are lots of implementation attacks
 
@@
 The lattice-based attacks presented here are based on the \textit{HNP (Hidden Number Problem)} introduced
-by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significan bits
+by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significant bits
 of $k$ can potentially leak the entire nonce \cite{ecdsa_nonce}.
 In 2020 a group of researcher were able to leak the MSBs of \textit{DH} and \textit{DHE} secrets in \textbf{TLS $\le$ 1.2}
-and using a similar lattice constructions as the one we will describe to solve the \textit{HNP}
-and thus breaks the protocol \cite{cryptoeprint:2020:1151} (Raccoon Attack).
+and used a similar lattice constructions as the one we will describe to solve the \textit{HNP}
+and thus break the protocol \cite{cryptoeprint:2020:1151} (Raccoon Attack).
 
@@
 \]
-
-Source of the method:
 
@@
 The most used cryptographic protocol used has been proved secure but it's very easy to implement them wrong and side-channel
-vulnerabilities can heavily compromise the security of the protocol.
+vulnerabilities can heavily compromise the security of the protocols.
 

### 2024-05-06 lattice_based_attacks.tex
version 2, fix grammar

--- 2021-06-04 paper.tex
@@
 % \usepackage{algorithm}% http://ctan.org/pkg/algorithms
-% \usepackage[ruled,vlined]{algorithm2e}
+% \usepackage[ruled, vlined]{algorithm2e}
 % \usepackage{algorithm}
 \usepackage[]{algorithm2e}
+\usepackage{titling}
 \usepackage{algorithmic}
@@
 \newcommand{\dd}{\cdot}
-
-\title{Introduction to Lattice-based Attacks\\``Cryptography''}
-
-\author{Di Santi Giovanni}
-\date{\today}
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \par\end{center}
+    \begin{center}\large#1\end{center}
+    \vskip0.5em}
+}
+
+\title{Introduction to Lattice-based Attacks}
+\subtitle{Version 2}
+
+\author{Giovanni Di Santi}
+\date{}
 
@@
 
-Lattices are powerful mathematical objects that can be used in computer science and mathematics to solves an extensive range of different problems.
-In the recents years many post-quantum cryptographic protocols candidates involve the use of hard lattices problems,
-for example the \textbf{Learning With Errors} \cite{LWE}.
-Lattice constructions can also be used in cryptanalysis to break cryptographic schemes, typically using reduction
-algorithms as \textbf{LLL} \cite{LLL}.
-
-To introduce the mathematics of lattices a basic linear algebra background is needed, so the second chapter is a summary of the
-basics properties needed to understand it. We used as main resource ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
-explain them, but we also tried to gives some geometrical intuition behind some operations.
-
-Cryptographic protocol as \textbf{RSA} and \textbf{ECDSA} are considered secure, however there are various attacks against a
-relaxed-model of each of them, i.e., What if we know some bits of the secret key? What if we know a part of the message before the encryption?
-We present an introduction to the attacks which involves lattices against these protocols. The code used to confirm the correctness
-of the attacks is available on the repository \cite{repo} and the main reference was
+Lattices are potent mathematical structures widely utilized in computer science and mathematics to solve a broad spectrum of problems.
+In recent years, numerous post-quantum cryptographic protocol candidates have employed the challenging problems associated with hard lattices,
+for example, the \textbf{Learning With Errors} \cite{LWE}.
+Additionally, lattice constructions are leveraged in cryptanalysis to compromise cryptographic schemes, typically through the use of
+reduction algorithms such as \textbf{LLL} \cite{LLL}.
+
+To comprehend the mathematics of lattices, a foundational understanding of linear algebra is essential. Therefore, the second chapter provides a summary of the
+basic properties necessary for this understanding. We primarily referenced ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
+elucidate these concepts, while also providing some geometric intuition behind certain operations.
+
+Cryptographic protocols such as \textbf{RSA} and \textbf{ECDSA} are considered secure; however, various attacks can exploit a
+relaxed model of each, e.g., what if some bits of the secret key are known? What if a portion of the message is known prior to encryption?
+We introduce lattice-based attacks on these protocols and provide code in our repository \cite{repo} to verify the effectiveness of these attacks. The main reference for this discussion is
 ``Recovering cryptographic keys from partial information, by example''\cite{cryptoeprint:2020:1506}.
 
+% Lattices are powerful mathematical objects that can be used in computer science and mathematics to solves an extensive range of different problems.
+% In the recent years many post-quantum cryptographic protocols candidates involve the use of hard lattices problems,
+% for example the \textbf{Learning With Errors} \cite{LWE}.
+% Lattice constructions can also be used in cryptanalysis to break cryptographic schemes, typically using reduction
+% algorithms as \textbf{LLL} \cite{LLL}.
+% 
+% To introduce the mathematics of lattices a basic linear algebra background is needed, so the second chapter is a summary of the
+% basics properties needed to understand it. We used as main resource ``An Introduction to Mathematical Cryptography''\cite{mathcrypto14} to
+% explain them, but we also tried to give some geometrical intuition behind some operations.
+% 
+% Cryptographic protocol as \textbf{RSA} and \textbf{ECDSA} are considered secure, however there are various attacks against a
+% relaxed-model of each of them, i.e., What if we know some bits of the secret key? What if we know a part of the message before the encryption?
+% We present an introduction to the attacks which involves lattices against these protocols. The code used to confirm the correctness
+% of the attacks is available on the repository \cite{repo} and the main reference was
+% ``Recovering cryptographic keys from partial information, by example''\cite{cryptoeprint:2020:1506}.
+
 \chapter{Linear Algebra Background}
 
-We'll start with some definitions and properties needed to understand the lattices, to move later on the mathematics behind them and some
-hard problems related to it. At the end of the chapter the reader should be able to follow the math used in the other chapters.
+This chapter introduces key definitions and properties essential for understanding lattices.
+It progresses to cover the mathematics of lattices and related complex problems.
+By the end of this chapter, the reader should be well-equipped to follow the mathematical discussions in subsequent chapters.
 
@@
 \end{definition}
-A \textit{vector space} $V$ is a subset of $\R^{m}$ which is closed under finite vector addition and scalar multiplication, with the property that
-
-\begin{center}
-   $a_1v_1 + a_2v_2 \in V$ for all $v_1,v_2 \in V$ and all $a_1,a_2 \in \R$
+A \textit{vector space} $V$ over $\R^{m}$ is a set closed under finite vector addition and scalar multiplication. This closure is characterized by:
+
+\begin{center}
+   $a_1v_1 + a_2v_2 \in V$ for any $v_1,v_2 \in V$ and $a_1,a_2 \in \R$
 \end{center}
@@
 
-Let $v_1,v_2,\ldots,v_k \in V$. A \textit{linear combination} of $v_1,v_2,\ldots,v_k \in V$ is any vector of the form
-
-\begin{center}
-    $\alpha_1v_1 + \alpha_2v_2 + \cdots + \alpha_kv_k$ with $\alpha_1, \ldots, \alpha_k \in \R$
+Consider any vectors $v_1, v_2, \ldots, v_k \in V$. A \textit{linear combination} of these vectors is any vector expressed as:
+
+\begin{center}
+    $\alpha_1v_1 + \alpha_2v_2 + \cdots + \alpha_kv_k$ where $\alpha_1, \ldots, \alpha_k \in \R$
 \end{center}
@@
 \begin{definition}
-    \textbf{Linear Independece}
+    \textbf{Linear Independence}
 \end{definition}
 
-A set of vectors $v_1,v_2,\ldots,v_k \in V$ is \textit{linearly independent} if the the only way to get
+A set of vectors $v_1, v_2, \ldots, v_k \in V$ is \textit{linearly independent} if the only solution to the equation
 
@@
 
-is to have $a_1 = a_2 = \cdots = a_k = 0$.
+is $a_1 = a_2 = \cdots = a_k = 0$.
 
@@
 
-Taken a set of linearly independent vectors $b = (v_1,\ldots,v_n) \in V$ we say that $b$ is a \textit{basis} of $V$ if $\forall w \in V$ we can write
+A set of linearly independent vectors $b = (v_1, \ldots, v_n) \in V$ constitutes a \textit{basis} of $V$ if every vector $w \in V$ can be represented as:
 
@@
 \begin{definition}
-    \textbf{Vector's length}
+    \textbf{Vector's Length}
 \end{definition}
 
-The vector's length or \textit{Euclidean norm} of $v = (x_1, x_2, \ldots, x_m)$ is
+The \textit{Euclidean norm} or length of a vector $v = (x_1, x_2, \ldots, x_m)$ is given by:
 
@@
 \end{center}
+
+% \chapter{Linear Algebra Background}
+% 
+% We start with some definitions and properties needed to understand the lattices, to move later on the mathematics behind them and some
+% hard problems related to it. At the end of the chapter the reader should be able to follow the math used in the other chapters.
+% 
+% \section{Vector Spaces}
+% 
+% \begin{definition}
+%     \textbf{Vector space}.
+% \end{definition}
+% A \textit{vector space} $V$ is a subset of $\R^{m}$ which is closed under finite vector addition and scalar multiplication, with the property that
+% 
+% \begin{center}
+%    $a_1v_1 + a_2v_2 \in V$ for all $v_1,v_2 \in V$ and all $a_1,a_2 \in \R$
+% \end{center}
+% 
+% \begin{definition}
+%     \textbf{Linear Combinations}
+% \end{definition}
+% 
+% Let $v_1,v_2,\ldots,v_k \in V$. A \textit{linear combination} of $v_1,v_2,\ldots,v_k \in V$ is any vector of the form:
+% 
+% \begin{center}
+%     $\alpha_1v_1 + \alpha_2v_2 + \cdots + \alpha_kv_k$ with $\alpha_1, \ldots, \alpha_k \in \R$
+% \end{center}
+% 
+% \begin{definition}
+%     \textbf{Linear Independece}
+% \end{definition}
+% 
+% A set of vectors $v_1,v_2,\ldots,v_k \in V$ is \textit{linearly independent} if the the only way to get
+% 
+% \begin{center}
+%     $a_1v_1 + a_2v_2 + \cdots + a_kv_k = 0$
+% \end{center}
+% 
+% is to have $a_1 = a_2 = \cdots = a_k = 0$.
+% 
+% \begin{definition}
+%     \textbf{Bases}
+% \end{definition}
+% 
+% Taken a set of linearly independent vectors $b = (v_1,\ldots,v_n) \in V$ we say that $b$ is a \textit{basis} of $V$ if $\forall w \in V$ we can write
+% 
+% \begin{center}
+%     $w = a_1v_1 + a_2v_2 + \cdots + a_nv_n$
+% \end{center}
+% 
+% \begin{definition}
+%     \textbf{Vector's length}
+% \end{definition}
+% 
+% The vector's length or \textit{Euclidean norm} of $v = (x_1, x_2, \ldots, x_m)$ is
+% 
+% \begin{center}
+%     $\lVert v \rVert = \sqrt{x_1^2 + x_2^2 + \cdots + x_m^2}$
+% \end{center}
 
@@
 
-Let $v, w \in V \subset \R^m$ and $v = (x_1, x_2, \ldots, x_m), w = (y_1, y_2, \ldots, y_m)$, the \textit{dot product} of $v$ and $m$ is
-
-\begin{center}
-    $v \dd m = x_1y_1 + x_2y_2 + \cdots + x_my_m$
+Given vectors $v, w \in V \subset \R^m$ where $v = (x_1, x_2, \ldots, x_m)$ and $w = (y_1, y_2, \ldots, y_m)$, the \textit{dot product} of $v$ and $w$ is defined as:
+
+\begin{center}
+    $v \cdot w = x_1y_1 + x_2y_2 + \cdots + x_my_m$
 
@@
 
-    $v \dd m = \lVert v \rVert \lVert w \rVert \cos{\theta}$
-\end{center}
-
-where $\theta$ is the angle between $v$ and $w$ if we place the starting points of the vectors at the origin $O$.
+    $v \cdot w = \lVert v \rVert \lVert w \rVert \cos{\theta}$
+\end{center}
+
+where $\theta$ is the angle between $v$ and $w$ when their starting points are positioned at the origin $O$.
 
@@
 
-Geometrically speaking $v \cdot m$ is the length of $w$ projected to $v$ multiplied by the length of $v$ as shown in \ref{fig:dot_product}
+Geometrically, $v \cdot w$ represents the length of the projection of $w$ onto $v$ multiplied by the length of $v$, as illustrated in \ref{fig:dot_product}.
 
 \begin{definition}
-    \textbf{Ortoghonal Basis} 
+    \textbf{Orthogonal Basis}
 \end{definition}
 
-An \textit{ortoghonal basis} for a vector space $V$ is a basis $v_1, \ldots, v_m$ with the property that
-
-\begin{center}
-    $v_i \dd v_j = 0$ for all $i \neq j$
-\end{center}
-
-If $\lVert v_i \rVert = 1$ for all $i$ then the basis is \textit{orthonormal}.
+An \textit{orthogonal basis} for a vector space $V$ consists of vectors $v_1, \ldots, v_m$ such that:
+
+\begin{center}
+    $v_i \cdot v_j = 0$ for all $i \neq j$
+\end{center}
+
+If $\lVert v_i \rVert = 1$ for each $i$, then the basis is termed \textit{orthonormal}.
 
@@
     \vspace*{5px}
-    $v_1^* = v1$\;
+    $v_1^* = v_1$\;
     \\
@@
 
-Let $b = (v_1, \ldots, v_n)$, be a basis for a vector space $V \subset \R^m$. There is an algorithm to create an orthogonal basis
-$b^* = (v_1^*,\ldots,v_n^*)$.
-The two bases have the property that Span$\{v_1,\ldots,v_i\}$ = Span$\{v_1^*,\ldots,v_i^*\}$ for all $i = 1,2,\ldots,n$
+Given a basis $b = (v_1, \ldots, v_n)$ of a vector space $V \subset \R^m$, the Gram-Schmidt algorithm generates an orthogonal basis $b^* = (v_1^*,\ldots,v_n^*)$.
+These two bases satisfy the property that Span$\{v_1,\ldots,v_i\}$ = Span$\{v_1^*,\ldots,v_i^*\}$ for all $i = 1,2,\ldots,n$.
 
@@
     \includegraphics[width=0.5\textwidth]{./img/gram_schmidt.png}
-    \caption{Gram Schmidt orthogonalization}
+    \caption{Gram Schmidt Orthogonalization}
     \label{fig:gram_schmidt}
@@
 
-If we take $v_1=(4, 1), v_2=(2, 3)$ as basis and apply gram schmidt we obtain $u_1=v_1=(4, 1), u_2=(-10/17, 40/17)$ as shown in \ref{fig:gram_schmidt}
+Using vectors $v_1=(4, 1)$ and $v_2=(2, 3)$ as a basis and applying the Gram-Schmidt process results in $u_1=v_1=(4, 1), u_2=(-10/17, 40/17)$, as depicted in \ref{fig:gram_schmidt}.
 
@@
 
-The \textit{determinant} of a square matrix is a function that satisfies the following properties:
+The \textit{determinant} of a square matrix is a scalar value that characterizes the matrix and is defined by the following properties:
 
@@
     \item The determinant is linear in each row.
-    \item The determinant reverses sign if two rows are interchanged.
-    \item The determinant of the identity matrix is equal to 1.
+    \item The determinant changes sign when two rows are swapped.
+    \item The determinant of the identity matrix is 1.
 \end{enumerate}
 
-If the determinant of a matrix is $0$ then the matrix is called \textbf{singular} (without an inverse).\\
-
-Grant Sanderson created fantastic animations to understand the geometrical intuition behind the \textit{determinant}\cite{determinant}.
+A matrix is termed \textbf{singular} if its determinant is $0$, indicating it lacks an inverse.\\
+
+Animations created by Grant Sanderson provide a fantastic visual understanding of the geometric intuition behind the \textit{determinant}\cite{determinant}.
+
+% \begin{definition}
+%     \textbf{Dot Product}
+% \end{definition}
+% 
+% Let $v, w \in V \subset \R^m$ and $v = (x_1, x_2, \ldots, x_m), w = (y_1, y_2, \ldots, y_m)$, the \textit{dot product} of $v$ and $m$ is
+% 
+% \begin{center}
+%     $v \dd m = x_1y_1 + x_2y_2 + \cdots + x_my_m$
+% 
+%     or
+% 
+%     $v \dd m = \lVert v \rVert \lVert w \rVert \cos{\theta}$
+% \end{center}
+% 
+% where $\theta$ is the angle between $v$ and $w$ if we place the starting points of the vectors at the origin $O$.
+% 
+% \begin{figure}[!b]
+%     \centering
+%     \includegraphics[scale=0.2]{./img/dot_product.png}
+%     \caption{Dot Product By 3Blue1Brown \cite{3b1b}}
+%     \label{fig:dot_product}
+% \end{figure}
+% 
+% Geometrically speaking $v \cdot m$ is the length of $w$ projected to $v$ multiplied by the length of $v$ as shown in \ref{fig:dot_product}
+% 
+% \begin{definition}
+%     \textbf{Ortoghonal Basis} 
+% \end{definition}
+% 
+% An \textit{ortoghonal basis} for a vector space $V$ is a basis $v_1, \ldots, v_m$ with the property that
+% 
+% \begin{center}
+%     $v_i \dd v_j = 0$ for all $i \neq j$
+% \end{center}
+% 
+% If $\lVert v_i \rVert = 1$ for all $i$ then the basis is \textit{orthonormal}.
+% 
+% \begin{algorithm}[H]
+%     \vspace*{5px}
+%     $v_1^* = v1$\;
+%     \\
+%     \For{$i \gets 2$ \KwTo $n$}{
+%         $\mu_{ij} = v_i \cdot v_j^* / \lVert v_j^* \rVert ^ 2$ for $1 \le j < i$ \;
+%         \\
+%         $v_i^* = v_i - \sum_{j=1}^{i-1} \mu_{ij}v_j^*$ \;
+%     }
+%     \caption{Gram-Schmidt Algorithm}
+%     \label{alg:gram_schmidt}
+% \end{algorithm}
+% 
+% Let $b = (v_1, \ldots, v_n)$, be a basis for a vector space $V \subset \R^m$. There is an algorithm to create an orthogonal basis
+% $b^* = (v_1^*,\ldots,v_n^*)$.
+% The two bases have the property that Span$\{v_1,\ldots,v_i\}$ = Span$\{v_1^*,\ldots,v_i^*\}$ for all $i = 1,2,\ldots,n$
+% 
+% \begin{figure}[htpb]
+%     \centering
+%     \includegraphics[width=0.5\textwidth]{./img/gram_schmidt.png}
+%     \caption{Gram Schmidt orthogonalization}
+%     \label{fig:gram_schmidt}
+% \end{figure}
+% 
+% If we take $v_1=(4, 1), v_2=(2, 3)$ as basis and apply gram schmidt we obtain $u_1=v_1=(4, 1), u_2=(-10/17, 40/17)$ as shown in \ref{fig:gram_schmidt}
+% 
+% \begin{definition}
+%     \textbf{Determinant}
+% \end{definition}
+% 
+% The \textit{determinant} of a square matrix is a function that satisfies the following properties:
+% 
+% \begin{enumerate}
+%     \item The determinant is linear in each row.
+%     \item The determinant reverses sign if two rows are interchanged.
+%     \item The determinant of the identity matrix is equal to 1.
+% \end{enumerate}
+% 
+% If the determinant of a matrix is $0$ then the matrix is called \textbf{singular} (without an inverse).\\
+% 
+% Grant Sanderson created fantastic animations to understand the geometrical intuition behind the \textit{determinant}\cite{determinant}.
+
+% \section{Lattices}
+% 
+% \begin{definition}
+%     \textbf{Lattice}
+% \end{definition}
+% 
+% Let $v_1,\ldots,v_n \in \R^m, m \ge n$ be linearly independent vectors. A \textit{Lattice} $L$ spanned by $\{v_1,\ldots,n_n\}$ is the set of 
+% all integer linear combinations of $v_1,\ldots,v_n$.
+% 
+% \begin{center}
+%     $L = \bigg\{\sum_{i=1}^{n} a_iv_i, a_i \in \Z \bigg\}$
+% \end{center}
+% 
+% If $v_i$ for every $i = 1,\ldots\,n$ has integer coordinates then the lattice is
+% called \textit{Integral Lattice}.
+% 
+% On the figure \ref{fig:lattice0} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$, and on \ref{fig:lattice1} the same lattice $L$ with
+% a different basis.
+% 
+% \begin{figure}[!bp]
+%     \begin{minipage}[b]{0.50\textwidth}
+%         \includegraphics[width=\textwidth]{./img/lattice_b0.png}
+%         \caption{Lattice $L$ spanned by $v, w$}
+%         \label{fig:lattice0}
+%     \end{minipage}
+%     \hspace{\fill}
+%     \hspace{\fill}
+%     \hspace{\fill}
+%     \hspace{\fill}
+%     \hspace{\fill}
+%     \begin{minipage}[b]{0.50\textwidth}
+%         \includegraphics[width=\textwidth]{./img/lattice_b1.png}
+%         \caption{Lattice $L$ spanned by $v', w'$}
+%         \label{fig:lattice1}
+%     \end{minipage}
+% \end{figure}
+% 
+% \clearpage
+% 
+% \section{Lattice Problems}
+% 
+% \subsection{SVP}
+% 
+% \textbf{The Shortest Vector Problem} (\texttt{SVP}): \textit{Find a nonzero vector $v \in L$ that minimez the Euclidean norm $\lVert v \rVert$.}
+% 
+% Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
+% gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.
+% 
+% \begin{figure}[!b]
+%     \centering
+%     \includegraphics[width=0.6\textwidth]{./img/gauss_svp.png}
+%     \caption{Gauss reduction}
+%     \label{fig:gauss_svp}
+% \end{figure}
+% 
+% \begin{algorithm}[H]
+%     \vspace*{5px}
+%     \While{true}{
+%         \If{$\lVert v_2 \rVert < \lVert v_1 \rVert$}{
+%             swap $v_1, v_2$ \;
+%         }
+%         m = $\left \lfloor{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rfloor$ \\
+%         \If{$m = 0$}{
+%             return $v_1, v_2$ \;
+%         }
+%         $v_2 = v_2 - mv_1$ \\
+%     }
+%     \caption{Gauss Basis Reduction}
+% \end{algorithm}
+% 
+% \textbf{Example}. Let $L$ a lattice spanned by $v_1 = (8, 4), v_2 = (7, 5)$, if we apply the gauss reduction algorithm we
+% obtain $w_1 = (1, -1), w_2 = (6, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$.
+% 
+% The bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to solve it.
+% 
+% \subsection{CVP}
+% 
+% \textbf{The Closest Vector Problem} (\texttt{CVP}): \textit{Given a vector $t \in \R^m$ that is not in $L$, find the vector $v \in L$
+%     closest to $t$, in other words find a vector $v \in L$ that minimizes the Euclidean norm $\lVert t - v \rVert$.}
+% 
+% \begin{figure}[!ht]
+%     \centering
+%     \includegraphics[width=0.6\textwidth]{./img/cvp.png}
+%     \caption{CVP}
+%     \label{fig:cvp}
+% \end{figure}
+% 
+% \textbf{Example}. Let $L$ a lattice spanned by $v_1 = (0, 1), v_2 = (2, 0)$, and a target vector $t = (2.3, 2.4)$. The closest vector
+% to $t$ in the lattice $L$ is $w = (2, 2)$.\\
+% 
+% Both \textbf{CVP} and \textbf{SVP} are $\mathcal{NP}$-hard problems, thus the complexity of the problem increments with the dimension
+% of the lattice. They can be used as primitive to create a trapdoor functions for a cryptographic scheme.
+% 
+% There are various algorithms that can output a solution under certain constraints for an approximation of both \textbf{SVP}
+% and \textbf{CVP}, for example \textbf{LLL}\cite{LLL} and \textbf{Babai's algorithm}\cite{babai} respectively.
 
@@
 
-Let $v_1,\ldots,v_n \in \R^m, m \ge n$ be linearly independent vectors. A \textit{Lattice} $L$ spanned by $\{v_1,\ldots,n_n\}$ is the set of 
-all integer linear combinations of $v_1,\ldots,v_n$.
-
-\begin{center}
-    $L = \bigg\{\sum_{i=1}^{n} a_iv_i, a_i \in \Z \bigg\}$
-\end{center}
-
-If $v_i$ for every $i = 1,\ldots\,n$ has integer coordinates then the lattice is
-called \textit{Integral Lattice}.
-
-On the figure \ref{fig:lattice0} we show a lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$, and on \ref{fig:lattice1} the same lattice $L$ with
-a different basis.
-
-\begin{figure}[!tbp]
+Consider $v_1, \ldots, v_n \in \R^m$ with $m \ge n$, which are linearly independent vectors.
+A \textit{lattice} $L$, spanned by $\{v_1, \ldots, v_n\}$, comprises all integer linear combinations of these vectors:
+
+\begin{center}
+    $L = \bigg\{\sum_{i=1}^{n} a_iv_i , a_i \in \Z \bigg\}$
+\end{center}
+
+If every $v_i$ ($i = 1, \ldots, n$) has integer coordinates, the lattice is termed an \textit{integral lattice}.
+
+Figures \ref{fig:lattice0} and \ref{fig:lattice1} depict the lattice $L$ with bases $v=(3, 1)$ and $w=(-1, 1)$, and another basis configuration, respectively.
+
+\begin{figure}[H]
     \begin{minipage}[b]{0.50\textwidth}
@@
     \end{minipage}
-    \hspace{\fill}
-    \hspace{\fill}
-    \hspace{\fill}
-    \hspace{\fill}
     \hspace{\fill}
@@
 
-\clearpage
-
 \section{Lattice Problems}
@@
 
-\textbf{The Shortest Vector Problem} (\texttt{SVP}): \textit{Find a nonzero vector $v \in L$ that minimez the Euclidean norm $\lVert v \rVert$.}
-
-Gauss's developed an algorithm to find an optimal basis for a two-dimensional lattice given an arbitrary basis. The output of the algorithm
-gives the shortest nonzero vector in $L$ and in this way solves the \texttt{SVP}.
+\textbf{The Shortest Vector Problem} (\texttt{SVP}): \textit{Find a nonzero vector $v \in L$ that minimizes the Euclidean norm $\lVert v \rVert$.}
+
+Gauss developed an algorithm to determine an optimal basis for a two-dimensional lattice from any given basis. This method outputs the shortest nonzero vector in $L$, thereby solving the \texttt{SVP}.
 
@@
         \If{$\lVert v_2 \rVert < \lVert v_1 \rVert$}{
-            swap $v_1, v_2$ \;
+            swap $v_1, v_2$\;
         }
-        m = $\left \lfloor{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rfloor$ \\
+        m = $\left \lfloor{(v_1 \cdot v_2) {\lVert v_1 \rVert}^{-2}} \right \rfloor$\;
         \If{$m = 0$}{
-            return $v_1, v_2$ \;
+            return $v_1, v_2$\;
         }
-        $v_2 = v_2 - mv_1$ \\
+        $v_2 = v_2 - mv_1$\;
     }
@@
 
-\textbf{Example}. Let $L$ a lattice spanned by $v_1 = (8, 4), v_2 = (7, 5)$, if we apply the gauss reduction algorithm we
-obtain $w_1 = (1, -1), w_2 = (6, 6)$ \ref{fig:gauss_svp}. $w_1$ is the shortest nonzero vector in the lattice $L$.
-
-The bigger the dimension of the lattice, the harder is the problem and there isn't a polynomial algorithm to solve it.
+\textbf{Example}: In a lattice $L$ spanned by $v_1 = (8, 4), v_2 = (7, 5)$, applying the Gauss reduction algorithm results in $w_1 = (1, -1), w_2 = (6, 6)$ as shown in \ref{fig:gauss_svp}.
+$w_1$ represents the shortest nonzero vector in lattice $L$.
+
+The complexity of solving \texttt{SVP} increases with the dimension of the lattice, making it a challenging problem without a known polynomial-time solution.
 
@@
 
-\textbf{The Closest Vector Problem} (\texttt{CVP}): \textit{Given a vector $t \in \R^m$ that is not in $L$, find the vector $v \in L$
-    closest to $t$, in other words find a vector $v \in L$ that minimizes the Euclidean norm $\lVert t - v \rVert$.}
+\textbf{The Closest Vector Problem} (\texttt{CVP}): \textit{Given a vector $t \in \R^m$ that is not in $L$, find the vector $v \in L$ closest to $t$, minimizing the Euclidean norm $\lVert t - v \rVert$.}
 
@@
 
-\texbtf{Example}. Let $L$ a lattice spanned by $v_1 = (0, 1), v_2 = (2, 0)$, and a target vector $t = (2.3, 2.4)$. The closest vector
-to $t$ in the lattice $L$ is $w = (2, 2)$.\\
-
-Both \textbf{CVP} and \textbf{SVP} are $\mathcal{NP}$-hard problems, thus the complexity of the problem increments with the dimension
-of the lattice. They can be used as primitive to create a trapdoor functions for a cryptographic scheme.
-
-There are various algorithms that can output a solution under certain constraints for an approximation of both \textbf{SVP}
-and \textbf{CVP}, for example \textbf{LLL}\cite{LLL} and \textbf{Babai's algorithm}\cite{babai} respectively.
+\textbf{Example}: For a lattice $L$ spanned by $v_1 = (0, 1), v_2 = (2, 0)$, with target vector $t = (2.3, 2.4)$, the closest vector in the lattice $L$ is $w = (2, 2)$, as depicted in \ref{fig:cvp}.
+
+Both \textbf{CVP} and \textbf{SVP} are considered $\mathcal{NP}$-hard problems, and their complexity increases with the dimension of the lattice.
+They serve as primitives for creating trapdoor functions in cryptographic schemes.
+
+Several algorithms can approximate solutions for both \textbf{SVP} and \textbf{CVP}, such as \textbf{LLL}\cite{LLL} and \textbf{Babai's algorithm}\cite{babai} respectively.
 
@@
 
-The \textbf{Lenstra-Lenstra-Lovász} \textit{LLL}\cite{LLL} or \textit{$L^3$} is a polynomial time algorithm to find a ``short'' basis of a lattice.
+The \textbf{Lenstra-Lenstra-Lovász (LLL)} algorithm is a polynomial-time method designed to compute a "short" basis for a lattice.
 
@@
 
-\textit{Let $L \in \Z^n$ be a lattice spanned by $B = \{v_1,\ldots,v_n\}$. The LLL algorithm outputs a reduced lattice
-basis $\{w_1, \ldots, w_n\}$ with}
-
-\begin{center}
-    $\lVert w_i \rVert \le 2^{\frac{n(n-1)}{4(n-i+1)}} det(L)^{\frac{1}{n-i+1}}$ for $i=1,\ldots,n$
-\end{center}
-
-\textit{in time polynomial in n and in the bit-size of the entries of the basis matrix $B$}.\\
-
-Basically the first vector of the new basis will be as short as possible, and the other will have increasing lengths. The new vectors
-will be as orthogonal as possible to one another, i.e., the dot product $w_i \dd w_j$ will be close to zero.
+Given a lattice $L \in \Z^n$ spanned by $B = \{v_1,\ldots,v_n\}$, the LLL algorithm produces a reduced basis $\{w_1, \ldots, w_n\}$ such that:
+
+\begin{center}
+    $\lVert w_i \rVert \le 2^{\frac{n(n-1)}{4(n-i+1)}} \cdot det(L)^{\frac{1}{n-i+1}}$ for $i=1,\ldots,n$
+\end{center}
+
+This process is executed in time polynomial in $n$ and the bit-size of the entries in the basis matrix $B$.\\
+
+In this reduced basis, the vectors are as short as possible starting from the first, with each subsequent vector being longer.
+Additionally, these vectors are almost orthogonal to each other, meaning the dot product $w_i \cdot w_j$ is close to zero.
 
@@
 
-For example we can take the following basis (the rows are the vector) that span
-a lattice $L$.
+Consider the following basis, represented in matrix form, that spans a lattice $L$:
 
@@
 
-Applying the LLL algorithm we obtain
+After applying the LLL algorithm, the basis is transformed to:
 
@@
 
-Where the first row is the shortest vector in the lattice $L$, and so solves the \textbf{SVP} problem.
-For higher dimensions however the LLL algorithm outputs only an approximation for the \textbf{SVP} problem.
+Here, the first row is the shortest vector in the lattice $L$, thus addressing the \textbf{SVP} problem.
+For higher dimensions, however, the LLL algorithm provides only an approximation to the \textbf{SVP}.
 
@@
     \vspace*{5px}
-    $\mu_{i,j}$ is the quantity $(v_i \cdots v_j^*) / \lVert v_j^* \rVert^2$. \\
+    $\mu_{i,j}$ is the quantity $(v_i \cdot v_j^*) / \lVert v_j^* \rVert^2$. \\
     Output reduced basis ${v_1, \ldots, v_n}$
@@
 
-The running time of the algorithm is polynomial and executes the main loop no more than
+The running time of the algorithm is polynomial and completes the main loop in no more than
 $\mathcal{O}(n^2\log n + n^2\log M)$ steps, where $M = max \lVert v_i \rVert$. \\
 
-Kelby Ludwig explains an intuition behind every steps of the algorithm \cite{lllintuition}, and Oded Regev
-gives a more rigorous explanation of the algorithm and the properties \cite{lllexplanation}.\\
-
-Some of the applications of the algorithm are the following:
+Kelby Ludwig elucidates the intuition behind each step of the algorithm \cite{lllintuition}, and Oded Regev provides a detailed explanation of its properties \cite{lllexplanation}.\\
+
+Applications of the LLL algorithm include:
 
 \begin{enumerate}
-    \item Factoring polynomials over the integers. For example, given $x^2 - 1$ factor it into $x + 1$ and $x - 1$.
-    \item Integer Programming. This is a well-known $\mathcal{NP}$-complete problem. Using \textbf{LLL}, one can obtain a polynomial time solution
-          to integer programming with a fixed number of variables.
-    \item Approximation to the \textbf{CVP} or \textbf{SVP}, as well as other lattice problems.
-    \item Cryptanalysis (break cryptographic protocols).
+    \item Factoring polynomials over the integers, e.g., factorizing $x^2 - 1$ into $(x + 1)(x - 1)$.
+    \item Solving Integer Programming, a renowned $\mathcal{NP}$-complete problem, in polynomial time when the number of variables is fixed.
+    \item Approximating solutions to the \textbf{CVP} and \textbf{SVP}, among other lattice-based challenges.
+    \item Cryptanalysis, specifically breaking cryptographic protocols.
 \end{enumerate}
 
+% \chapter{LLL}
+% 
+% \section{Introduction}
+% 
+% The \textbf{Lenstra-Lenstra-Lovász} \textit{LLL}\cite{LLL} or \textit{$L^3$} is a polynomial time algorithm to find a ``short'' basis of a lattice.
+% 
+% \begin{theorem}
+%     \textbf{LLL}
+% \end{theorem}
+% 
+% \textit{Let $L \in \Z^n$ be a lattice spanned by $B = \{v_1,\ldots,v_n\}$. The LLL algorithm outputs a reduced lattice
+% basis $\{w_1, \ldots, w_n\}$ with}
+% 
+% \begin{center}
+%     $\lVert w_i \rVert \le 2^{\frac{n(n-1)}{4(n-i+1)}} det(L)^{\frac{1}{n-i+1}}$ for $i=1,\ldots,n$
+% \end{center}
+% 
+% \textit{in time polynomial in n and in the bit-size of the entries of the basis matrix $B$}.\\
+% 
+% Basically the first vector of the new basis will be as short as possible, and the other will have increasing lengths. The new vectors
+% will be as orthogonal as possible to one another, i.e., the dot product $w_i \dd w_j$ will be close to zero.
+% 
+% \subsection*{Example}
+% 
+% For example we can take the following basis (the rows are the vector) that span
+% a lattice $L$.
+% 
+% \[
+% L = 
+% \begin{pmatrix}
+%     4 & 9 & 10\\
+%     2 & 1 & 30\\ 
+%     3 & 7 & 9
+% \end{pmatrix}
+% \] 
+% 
+% Applying the LLL algorithm we obtain
+% 
+% \[
+% LLL(L) = 
+% \begin{pmatrix}
+%     -1 & -2 & -1\\
+%      3 & -2 &  1\\
+%     -1 & -1 &  5
+% \end{pmatrix}
+% \] 
+% 
+% Where the first row is the shortest vector in the lattice $L$, and so solves the \textbf{SVP} problem.
+% For higher dimensions however the LLL algorithm outputs only an approximation for the \textbf{SVP} problem.
+% 
+% \section{Algorithm}
+% 
+% \begin{algorithm}[H]
+%     \vspace*{5px}
+%     Input basis ${v_1, \ldots, v_n}$ \; \\
+%     $k = 2$ \; \\
+%     $v_1* = v_1$ \; \\
+%     \While{$k \le n$}{
+%         \For{$j = k -1$ \KwTo $1$ step $-1$} {
+%             $v_k = v_k - \left\lfloor\mu_{k, j}\right\rceil \boldsymbol{v}_{j}$  [size-reduction] \;
+%         }
+%         \eIf{$\lVert v_k^* \rVert^2 \ge (\frac{3}{4} - \mu_{k, k-1}^2) \lVert v_{k-1}^2 \rVert$}{
+%             $k = k + 1$ \;  [Lovàsz-condition]
+%         }{
+%             Swap $v_{k-1}$ and $v_k$ [swap-step] \; \\
+%             $k = \max(k - 1, 2)$
+%         }
+%     }
+%     Note: At each step, $v_1^*, \ldots, v_k^*$ is the orthogonalized set of vectors
+%     obtained with the Gram-Schmidt \ref{alg:gram_schmidt}. \\
+%     \vspace*{5px}
+%     $\mu_{i,j}$ is the quantity $(v_i \cdots v_j^*) / \lVert v_j^* \rVert^2$. \\
+%     Output reduced basis ${v_1, \ldots, v_n}$
+%     \caption{LLL reduction algorithm}
+% \end{algorithm}
+% 
+% The running time of the algorithm is polynomial and executes the main loop no more than
+% $\mathcal{O}(n^2\log n + n^2\log M)$ steps, where $M = max \lVert v_i \rVert$. \\
+% 
+% Kelby Ludwig explains an intuition behind every step of the algorithm \cite{lllintuition}, and Oded Regev
+% gives a more rigorous explanation of the algorithm and the properties \cite{lllexplanation}.\\
+% 
+% Some applications of the algorithm are the following:
+% 
+% \begin{enumerate}
+%     \item Factoring polynomials over the integers. For example, given $x^2 - 1$ factor it into $x + 1$ and $x - 1$.
+%     \item Integer Programming. This is a well-known $\mathcal{NP}$-complete problem. Using \textbf{LLL}, one can obtain a polynomial time solution
+%           to integer programming with a fixed number of variables.
+%     \item Approximation to the \textbf{CVP} or \textbf{SVP}, as well as other lattice problems.
+%     \item Cryptanalysis (break cryptographic protocols).
+% \end{enumerate}
+
 \chapter{RSA Cryptanalysis}
@@
 \textbf{RSA} is one of the earliest and most used asymmetric cryptosystem.
-The usual step to generate a public/private key for \textbf{RSA} is the following
+The steps to generate a public/private key for \textbf{RSA} are:
 
@@
 
-To encrypt a message $m$ with \textbf{textbook RSA}
+To encrypt a message $m$ with \textbf{textbook RSA}:
 
@@
 
-To decrypt a ciphertext $c$
+To decrypt a ciphertext $c$:
 
@@
 
-RSA relies on the hardness of factoring the modulo $N$ and we don't have a polynomial algorithm to factor it, so it's considered secure.
-However there are different attacks against textbook RSA or bad implementations:
+RSA relies on the hardness of factoring $N$, and there isn't a polynomial algorithm for factorization, so it's considered secure.
+However, there are different attacks against textbook RSA or bad implementations:
 
 \begin{itemize}
-    \item If $m < N^{\frac{1}{e}}$, then $m^e < N$ and the modulo operation is not applied and we only need to find the $e$th root of $c$ over the
-        integers to find $m$.
-    \item If $q = p + x$ where $x$ is small enough than it's easy to recover the factors of $N$ computing $A = \sqrt{N}$ and compute
-            $p = A - x$ for different value of $x$ until $N \mod p = 0$, then we have found $q = N / p$.
-    \item It's possible to recover $d$ if it is too small (for example to accelerate decryption) using the Wiener's attack \cite{wiener}.
+    \item If $m < N^{\frac{1}{e}}$, then $m^e < N$ (the modulo operation is not applied), and we only need to find the $e$th root of $c$ over the
+        integers to find $m$. This is one of the reasons why we pad the message before the encryption.
+    \item If $q = p + x$ where $x$ is small enough, then it's easy to recover the factors of $N$ computing $A = \sqrt{N}$ and 
+            $p = A - x$ for different values of $x$ until $N \mod p = 0$, which means that $q = N / p$.
+    \item It's possible to recover $d$ if it is too small (in practice it could be used to accelerate decryption), using the Wiener's attack \cite{wiener}.
     \item Other attacks can be found on the excellent survey by Dan Boneh \cite{boneh99twentyyears}.
@@
 
-We start introducing the main ideas of Coppersmith's attack \cite{coppersmith96} and the math behind it.
-The attack can be used against \textbf{RSA} when a small $e$ is used, but also
-to factorize the modulus if some bits of $p$ or $q$ are known. In 2017 the attack was used to exploit
-\href{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-15361}{CVE-2017-15361} also named \textbf{ROCA}
-(Return Of Coppersmith's Attack) \cite{roca}.
-
-\subsection{Mathematical introduction}
-
-It's easy to find the roots of a univariate polynomial over the integers. Finding the roots of \textbf{modular} polynomial is hard, example:
+We begin by discussing the main concepts behind Coppersmith's attack \cite{coppersmith96} and the underlying mathematics.
+This attack is applicable to \textbf{RSA} when a small exponent $e$ is used, and it can also be used to factorize the modulus if partial information about $p$ or $q$ is known.
+In 2017, this method was utilized to exploit \href{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-15361}{CVE-2017-15361}, also known as \textbf{ROCA} (Return Of Coppersmith's Attack) \cite{roca}.
+
+\subsection{Mathematical Introduction}
+
+Finding roots of a univariate polynomial over the integers is straightforward. However, finding roots of a modular polynomial, such as:
 
@@
 
-Suppose $N$ is an \textbf{RSA} modulus and we don't know the factorization of it. Let's have an univariate integer polynomial $f(x)$ with degree $n$
+poses significant challenges. Assume $N$ is an \textbf{RSA} modulus whose factorization is unknown. Consider a univariate integer polynomial $f(x)$ of degree $n$:
 
@@
 
-Coppersmith showed how we can recover the value $x_0$ such that $f(x_0) \equiv 0 \mod N$, with $x_0 < N^{\frac{1}{n}}$ in polynomial time
-using the following theorem
+Coppersmith demonstrated that it is possible to recover the value $x_0$ such that $f(x_0) \equiv 0 \mod N$, with $x_0 < N^{\frac{1}{n}}$, in polynomial time using the following theorem:
+
+\clearpage
 
@@
 
-\textit{Let $g(x)$ be an univariate polynomial with n monomials and $m$ be a positive integer.
-    If we have some restraint $X$ and the following equations hold}
+\textit{Let $g(x)$ be a univariate polynomial with $n$ monomials and $m$ be a positive integer. If we establish a constraint $X$ and the following conditions are satisfied:}
 
@@
 
-\textit{Then $g(x_0) = 0$ holds over the integers.}
-
-\vspace*{10px}
-
-This theorem states that is possible to compute the root of $f(x) \mod N$ if we can find a polynomial $g(x)$ that share the same root but modulo $N^m$.
-If \ref{eq:bound} and \ref{eq:pol} hold then we can simply compute the root of $g(x)$ over the integers to have the same root $x_0$
-such that $f(x_0) \equiv 0 \mod N$.
-
-Howgrave-Graham's idea is to find this polynomial $g$ by combining polynomials $p_i$ who also have $x_0$ as roots modulo $N^m$.
-
-\vspace*{10px}
-
-The \textbf{LLL} algorithm is fundamental because:
+\textit{Then $g(x_0) = 0$ is also valid over the integers.}
+
+This theorem enables the computation of the root of $f(x) \mod N$ by finding a polynomial $g(x)$ that shares the same root, but modulo $N^m$.
+If the conditions \ref{eq:bound} and \ref{eq:pol} are met, the root of $g(x)$ over the integers corresponds to the same root $x_0$ such that $f(x_0) \equiv 0 \mod N$.
+
+The idea behind Howgrave-Graham's method involves generating polynomials $p_i$ that also have $x_0$ as a root modulo $N^m$.
+
+The significance of the \textbf{LLL} algorithm in this context is two-fold:
 
 \begin{itemize}
-    \item It only does \textbf{integer linear operations} on the basis vectors.
-        In this way even if the basis is different it's only a linear combination of vector that still have $x_0$ as root
-        modulo $N^m$.
-    \item If we craft the lattice properly, the norm of shortest vector on the reduced basis will satisfy \ref{eq:pol}.
-        We know the length's bound of the shortest vector that LLL could find.
+    \item It conducts \textbf{integer linear operations} on basis vectors, ensuring that even if the basis changes, it remains a linear combination of vectors retaining $x_0$ as a root modulo $N^m$.
+    \item If the lattice is properly constructed, the norm of the shortest vector in the reduced basis will satisfy \ref{eq:pol}, allowing the algorithm to predict the length's bound of the shortest vector it can find.
 \end{itemize}
 
-We can easily create polynomials $p_i$ ($g_{i,j}$ and $h_i$)  sharing the same root $x_0$ over $N^m$ of $f$ where $\delta$ is the degree of $f$:
+Polynomials $p_i$ ($g_{i,j}$ and $h_i$) sharing the same root $x_0$ over $N^m$ of $f$, where $\delta$ is the degree of $f$, can be crafted as follows:
 
@@
 
-Applying \textbf{LLL} to a lattice constructed by the coefficients of \ref{eq:create_pol} we'll find a short vector $v = g(xX)$ that will
-satisfy \ref{eq:pol}. If we then take $g(x)$ we will be able to compute the root over the integer.
-
-\subsection{Recover plaintext with known MSB bits of $m$}
-
-We will use a simplified version of the Coppersmith's attack that works when the root is approximately less than $N^{\frac{1}{6}}$.
-
-\textbf{Problem setup}. Let $N$ be an \textbf{RSA} modulus of $97$-bit:
+Applying \textbf{LLL} to a lattice built from the coefficients of \ref{eq:create_pol}, we'll find a short vector $v = g(xX)$ that will satisfy \ref{eq:pol}.
+Consequently, if we then compute $g(x)$, we will be able to determine the root over the integers.
+
+% \section{Lattices against RSA}
+% 
+% We start introducing the main ideas of Coppersmith's attack \cite{coppersmith96} and the math behind it.
+% The attack can be used against \textbf{RSA} when a small $e$ is used, but also
+% to factorize the modulus if some bits of $p$ or $q$ are known. In 2017 the attack was used to exploit
+% \href{https://cve.mitre.org/cgi-bin/cvename.cgi?name=CVE-2017-15361}{CVE-2017-15361} also named \textbf{ROCA}
+% (Return Of Coppersmith's Attack) \cite{roca}.
+% 
+% \subsection{Mathematical introduction}
+% 
+% It's easy to find the roots of a univariate polynomial over the integers. Finding the roots of \textbf{modular} polynomial is hard, example:
+% 
+% \begin{center}
+%     $f(x) \equiv 0 \mod N$
+% \end{center}
+% 
+% Suppose $N$ is an \textbf{RSA} modulus, and we don't know the factorization of it. Let's have an univariate integer polynomial $f(x)$ with degree $n$
+% 
+% \begin{center}
+%     $f(x) = x^n + a_{n-1}x^{n-1} + a_{n-2}x^{n-2} + \cdots + a_1n + a_0$
+% \end{center}
+% 
+% Coppersmith showed how we can recover the value $x_0$ such that $f(x_0) \equiv 0 \mod N$, with $x_0 < N^{\frac{1}{n}}$ in polynomial time
+% using the following theorem
+% 
+% \clearpage
+% 
+% \begin{theorem}
+%     \textbf{Howgrave-Graham}
+% \end{theorem}
+% 
+% \textit{Let $g(x)$ be an univariate polynomial with n monomials and $m$ be a positive integer.
+%     If we have some restraint $X$ and the following equations hold}
+% 
+% \begin{center}
+%     \begin{eqnarray}
+%         g(x_0) \equiv 0 \mod N^m, |x_0| \le X \label{eq:bound} \\
+%          \lVert g(xX) \rVert < \frac{N^m}{\sqrt{n}} \label{eq:pol}
+%     \end{eqnarray}
+% \end{center}
+% 
+% \textit{Then $g(x_0) = 0$ holds over the integers.}
+% 
+% \vspace*{10px}
+% 
+% This theorem states that is possible to compute the root of $f(x) \mod N$ if we can find a polynomial $g(x)$ that share the same root but modulo $N^m$.
+% If \ref{eq:bound} and \ref{eq:pol} hold then we can simply compute the root of $g(x)$ over the integers to have the same root $x_0$
+% such that $f(x_0) \equiv 0 \mod N$.
+% 
+% Howgrave-Graham's idea is to find this polynomial $g$ by combining polynomials $p_i$ who also have $x_0$ as roots modulo $N^m$.
+% 
+% \vspace*{10px}
+% 
+% The \textbf{LLL} algorithm is fundamental because:
+% 
+% \begin{itemize}
+%     \item It only does \textbf{integer linear operations} on the basis vectors.
+%         In this way even if the basis is different it's only a linear combination of vector that still have $x_0$ as root
+%         modulo $N^m$.
+%     \item If we craft the lattice properly, the norm of the shortest vector on the reduced basis will satisfy \ref{eq:pol}.
+%         We know the length's bound of the shortest vector that LLL could find.
+% \end{itemize}
+% 
+% We can easily create polynomials $p_i$ ($g_{i,j}$ and $h_i$)  sharing the same root $x_0$ over $N^m$ of $f$ where $\delta$ is the degree of $f$:
+% 
+% \begin{center}
+%     \begin{eqnarray}
+%         g_{i,j}(x) &= x^j \cdot N^i \cdot f^{m-i}(x) \text{ for } i = 0,\hdots,m-1,\hspace{2mm} j=0,\hdots,\delta-1 \label{eq:create_pol} \\
+%         h_i(x) &= x^i \cdot f^m(x) \text{ for } i = 0,\hdots,t-1 
+%     \end{eqnarray}
+% \end{center}
+% 
+% Applying \textbf{LLL} to a lattice constructed by the coefficients of \ref{eq:create_pol} we'll find a short vector $v = g(xX)$ that will
+% satisfy \ref{eq:pol}. If we then take $g(x)$ we will be able to compute the root over the integer.
+
+\subsection{Recovering Plaintext with Known MSB Bits of $m$}
+
+We will employ a simplified version of Coppersmith's attack, effective when the root is approximately less than $N^{\frac{1}{6}}$.
+
+\textbf{Problem Setup}. Consider an \textbf{RSA} modulus $N$ of 97 bits:
 
@@
 
-Before the encryption the message $m$ is padded as
+Before encryption, the message $m$ undergoes padding:
 
@@
 
-where $||$ is the concatenation.
-
-The ciphertext is
+where $||$ denotes concatenation.
+
+The resulting ciphertext is:
 
@@
 
-Suppose that we don't know the factorization of $N$ and we would like to know the message $m$.
-We know the padding and that the message $m$ is 2 bytes long, composed by only ascii letters, so $m < \texttt{0x7b7b}$.
+Assuming the factorization of $N$ is unknown, our goal is to deduce the message $m$.
+We are aware of the padding and that the message $m$ is 2 bytes long, consisting only of ASCII characters, so $m < \texttt{0x7b7b}$.
 
@@
 
-Let's define
+Let's define:
 
@@
     a = \texttt{0xffffffffffffffffffffff0000}
-.\]
-
-which is the known padding string that got encrypted.
+\]
+
+as the known padded string that was encrypted.
 
@@
 
-Thus we have that $c = (a + m)^3 \mod N$, for an unkown small $m$.
-We can define $f(x) = (a + x)^3 - c$, and so we setup the problem to find a small root $m$ such that $f(m) \equiv 0 \mod N$
+This leads to the equation $c = (a + m)^3 \mod N$, for an unknown small $m$. We can then define $f(x) = (a + x)^3 - c$ and set up the problem to find a small root $m$ such that $f(m) \equiv 0 \mod N$:
 
@@
 
-\textbf{Lattice contruction}. Let the coefficients of $f$ be $f(x) = x^3 + f_2x^2 + f_1x + f_0$
-and $X = \texttt{0x7b7b}$ be the upper bound of the size of the root $m$. We can construct the matrix
+\textbf{Lattice Construction}. Let the coefficients of $f(x)$ be $f(x) = x^3 + f_2x^2 + f_1x + f_0$ and $X = \texttt{0x7b7b}$ be the upper bound for the root $m$. We can construct the matrix:
 
@@
 
-The rows of the matrix correspond to the coefficient vectors of the polynomials $f(x), Nx^2, Nx$ and $N$, furthermore we know
-that each polynomials will be 0 modulo $N$ if evaluated at $x = m$.
-We applied Howgrave-Graham with $m=1$ (the $N^m$ parameter not the message).\\
-With this lattice construction every vector is of the form $v = (v_3X^3, v_2X^2, v_1X, v_0)$, because any
-integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=0,..,\dim(B)-1$.
-
-\textbf{Apply LLL}. We then apply LLL to find the shortest vector of the reduced basis:
+Each row of this matrix corresponds to the coefficient vectors of the polynomials $f(x), Nx^2, Nx,$ and $N$, all evaluated at $x = m$ being 0 modulo $N$.
+We apply Howgrave-Graham with $m=1$ (the $N^m$ parameter, not the message).
+
+In this lattice setup, every vector is of the form $v = (v_3X^3, v_2X^2, v_1X, v_0)$, because any integer linear combination of the vectors in the lattice will respect the bound $X^i$ for $i=\dim(B)-1,..,0$.
+
+\textbf{Apply LLL}. We apply LLL to identify the shortest vector in the reduced basis:
 
@@
 
-We can construct the polynomial $g$ using the coefficients of $v$
+Using the coefficients of $v$, we construct the polynomial $g$:
 
@@
 
-We know that
+% \subsection{Recover plaintext with known MSB bits of $m$}
+% 
+% We will use a simplified version of the Coppersmith's attack that works when the root is approximately less than $N^{\frac{1}{6}}$.
+% 
+% \textbf{Problem setup}. Let $N$ be an \textbf{RSA} modulus of $97$-bit:
+% 
+% \begin{center}
+%     $N=\texttt{0x1a34992f64135aedaa0fe2bfd}$ and $e = 3$.
+% \end{center}
+% 
+% Before the encryption the message $m$ is padded as
+% 
+% \[
+%     z = pad || m = \texttt{0xffffffffffffffffffffff} || m
+% \]
+% 
+% where $||$ is the concatenation.
+% 
+% The ciphertext is
+% 
+% \[
+%     c = z^e \mod N = \texttt{0x11701d5479bcdef207cba6937}
+% \]
+% 
+% Suppose that we don't know the factorization of $N$, and we would like to know the message $m$.
+% We know the padding and that the message $m$ is 2 bytes long, composed by only ascii letters, so $m < \texttt{0x7b7b}$.
+% 
+% \vspace*{10px}
+% 
+% Let's define
+% 
+% \[
+%     a = \texttt{0xffffffffffffffffffffff0000}
+% .\] 
+% 
+% which is the known padding string that got encrypted.
+% 
+% \vspace*{10px}
+% 
+% Thus, we have that $c = (a + m)^3 \mod N$, for an unkown small $m$.
+% We can define $f(x) = (a + x)^3 - c$, and setup the problem to find a small root $m$ such that $f(m) \equiv 0 \mod N$
+% 
+% \begin{align*}
+%     f(x) = x^3 + \texttt{0x17d7f55d0c9dc5851af54957c}x^2 + \texttt{0x3cf96fed2ea927527a2ed329}x\\
+%     + \texttt{0x32882e547964b3bcf75d315e}
+% \end{align*}
+% 
+% \vspace*{10px}
+% 
+% \textbf{Lattice contruction}. Let the coefficients of $f$ be $f(x) = x^3 + f_2x^2 + f_1x + f_0$
+% and $X = \texttt{0x7b7b}$ be the upper bound of the size of the root $m$. We can construct the matrix
+% 
+% \[
+% B = 
+% \label{mat:lattice_rsa}
+% \begin{pmatrix}
+%     X^3 & f_2X^2 & f_1X & f_0 \\
+%     0 & NX^2 & 0 & 0 \\
+%     0 & 0 & NX & 0 \\
+%     0 & 0 & 0 & N
+% \end{pmatrix}
+% \] 
+% 
+% The rows of the matrix correspond to the coefficient vectors of the polynomials $f(x), Nx^2, Nx$ and $N$, furthermore we know
+% that each polynomial will be 0 modulo $N$ if evaluated at $x = m$.
+% We applied Howgrave-Graham with $m=1$ (the $N^m$ parameter not the message).\\
+% With this lattice construction every vector is of the form $v = (v_3X^3, v_2X^2, v_1X, v_0)$, because any
+% integer linear combination of the vector of the lattice will keep the bound $X^i$ for $i=\dim(B)-1,..,0$.
+% 
+% \textbf{Apply LLL}. We then apply LLL to find the shortest vector of the reduced basis:
+% 
+% \[
+%     \begin{split}
+%     v = (-\texttt{0xd55d67baf71d}X^3, \texttt{0x3cf3cca3200a58bf}X^2, \\
+%     \texttt{0x3854d44211e80f248449}X, -\texttt{0xec93bf51cf766f7b9f1e5e6})
+%     \end{split}
+% \]
+% 
+% We can construct the polynomial $g$ using the coefficients of $v$
+% 
+% \[
+%     \begin{split}
+%         g(x) = -\texttt{0xd55d67baf71d}x^3 +  \texttt{0x3cf3cca3200a58bf}x^2 \\
+%         \texttt{0x3854d44211e80f248449}x -\texttt{0xec93bf51cf766f7b9f1e5e6}
+%     \end{split}
+% \]
+
+Knowing that:
 
@@
 
-What we need to prove is that
+We need to verify that:
 
@@
 
-In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 2^{\frac{n(n-1)}{4(n)}} (\det B)^{\frac{1}{n}}$.
-If we ignore the $2^{\frac{3}{4}}$ factor (remember that $n = 4$), then we need to satisfy
+In this scenario, the determinant of $B$, $\text{det} B = X^6N^3$, and LLL is expected to find a short vector with $\lVert v \rVert \le 2^{\frac{n(n-1)}{4(n)}} (\det B)^{\frac{1}{n}}$.
+Neglecting the factor $2^{\frac{3}{4}}$ (given that $n = 4$), the requirement simplifies to:
 
@@
 
-We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solves for $X$ this will be satisfied when
-$X < (\frac{N}{16})^{\frac{1}{6}}$. We can consider the $\sqrt{4}$ an error term to have $X < N^{\frac{1}{6}}$.
-With the numbers we have this inequality is verified, however even if the bound of the shortest vector is larger we still have some possibilities to
-find the correct root.
-
-If we compute the root of $g(x)$ over the integers we obtain $m = \texttt{0x4142} = $ ``AB'' which is the correct result.\\
-
-This specific lattice works to find roots up to size $N^{\frac{1}{6}}$, so the same construction will work if we want to find
+We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$.
+Solving for $X$ under this constraint implies $X < (\frac{N}{16})^{\frac{1}{6}}$.
+Adjusting for the $\sqrt{4}$ as an error term allows $X < N^{\frac{1}{6}}$.
+This inequality holds with the given numbers; however, even if the bound of the shortest vector is larger, there remains a chance to find the correct root.
+
+Computing the root of $g(x)$ over the integers, we find $m = \texttt{0x4142} = $ ``AB'', which is the correct result.\\
+
+This specific lattice construction is effective for finding roots up to size $N^{\frac{1}{6}}$. Therefore, the same approach could be applied to recover:
 
 \begin{itemize}
-    \item $\approx$ 170 unkown bits of message from an RSA 1024-bit modulus
-    \item $\approx$ 341 unkown bits of message from an RSA 2048-bit modulus
-    \item $\approx$ 683 unkown bits of message from an RSA 4096-bit modulus
+    \item Approximately 170 unknown bits of a message from an RSA 1024-bit modulus.
+    \item Approximately 341 unknown bits of a message from an RSA 2048-bit modulus.
+    \item Approximately 683 unknown bits of a message from an RSA 4096-bit modulus.
 \end{itemize}
 
-To compute bigger root a bigger lattice with more polynomials generated with \ref{eq:create_pol} is needed,
-this method is better described in \cite{may2011} and a detailed implementation in sagemath by David Wong is available \cite{wong2015}.
-
-\subsection{Factorize modulus with known MSB bits of $p$}
-
-Lattices can also be used to factor a modulus $N$ knowing the most significant bits of one of the factor.
-Let $a = 2^lb$ where $b$ are the bits known of $p$, then $p = a + r$ for some small value of $r$.
-We can rewrite the problem to find the root $r$ of $f(x) = a + x \mod p$ such that $f(r) = p \equiv 0 \mod p$.
-Suppose that we know the bound of $r$ such that $|r| < X$ for some bound $X$.
-
-We can construct the following lattices
+For larger roots, a more extensive lattice incorporating additional polynomials generated with \ref{eq:create_pol} is required.
+This methodology is further elaborated in \cite{may2011}, with a detailed implementation in SageMath by David Wong \cite{wong2015}.
+
+\subsection{Factorizing the Modulus with Known MSB Bits of $p$}
+
+Lattices can also assist in factorizing a modulus $N$ if the most significant bits of one of its factors are known.
+Let $a = 2^lb$, where $b$ represents the known bits of $p$, then $p = a + r$ for some small $r$.
+We can reformulate this to find the root $r$ of $f(x) = a + x \mod p$ such that $f(r) = p \equiv 0 \mod p$.
+Assume we know $r$'s upper bound, $|r| < X$.
+
+We can configure the following lattice:
 
@@
 
-Notice that the rows correspond to the polynomials $x(x + a)$, $(x + a)$, $N$ and that each of these polynomials will
-be $0 \mod p$ when $x = r$. As before \ref{mat:lattice_rsa}, every polynomial is scaled by $X$ which is the upperbound.
-
-We need to verify that the shortest vector that we can with \textbf{LLL} will be less than $p$ because if $g(x) < p$,
-then by construction we can compute $g(r) = 0$ over the integers.
-In this case we have
+Each row corresponds to the polynomials $x(x + a)$, $(x + a)$, and $N$, each evaluated at $x = r$ being $0 \mod p$.
+Similar to \ref{mat:lattice_rsa}, every polynomial is scaled by $X$, the upper bound.
+
+The shortest vector found by \textbf{LLL} should be less than $p$ because if $g(x) < p$, then by construction $g(r) = 0$ over the integers can be computed. We calculate:
 
@@
 
-Solving for $X$ we obtain $X < p^{\frac{1}{3}}$, so this method works for every $|r| < p^{\frac{1}{3}}$.
-
-To find $r$ we just need to apply \textbf{LLL} and take the first vector (shortest) that will be of the form $v = (v_2X^2, v_1X, v_0)$.
-
-The last step is to construct $g(x) = v_2x^2 + v_1x + v_0$ (just divides every coefficient by $X^i$)
-and computes the roots over the integers to find $r$. We implemented the attack against a modulus
-of \texbtf{RSA}-$1024$ knowing the $160$ most significant bits of $p$. The attack can be expanded
-until $X < p^{\frac{1}{2}}$ with a bigger lattice.
-
-\subsection{Real world case study: ROCA}
-
-\textbf{ROCA}\cite{roca} is a vulnerability discovered in 2017 in a software library \textit{RSALib} in the generation
-of the public modulus for \textbf{RSA}. The attack is believed to affects millions of smart cards. The vulnerbality
-resides in the generation of prime numbers, since embedded devices don't have lots of computational resources a fast way
-was needed. Every prime generated has the following structure:
+Solving for $X$ gives $X < p^{\frac{1}{3}}$, indicating that this method is valid for every $|r| < p^{\frac{1}{3}}$.
+
+To pinpoint $r$, simply apply \textbf{LLL} and take the first vector (the shortest), which will have the form $v = (v_2X^2, v_1X, v_0)$.
+
+Finally, construct $g(x) = v_2x^2 + v_1x + v_0$ (adjust each coefficient by dividing by $X^i$) and compute the roots over the integers to find $r$.
+We executed this attack against an \textbf{RSA}-$1024$ modulus knowing the $160$ most significant bits of $p$.
+This strategy can be extended to $X < p^{\frac{1}{2}}$ with a larger lattice.
+
+% We know that
+% 
+% \[
+%     g(x_0) \equiv 0 \mod N, |x_0| \le X
+% \]
+% 
+% What we need to prove is that
+% 
+% \[
+%     \lVert g(xX) \rVert \le \frac{N}{\sqrt{n}}
+% \] 
+% 
+% In this example, det $B = X^6N^3$, and LLL will find a short vector with $\lVert v \rVert \le 2^{\frac{n(n-1)}{4(n)}} (\det B)^{\frac{1}{n}}$.
+% If we ignore the $2^{\frac{3}{4}}$ factor (remember that $n = 4$), then we need to satisfy
+% 
+% \[
+%     g(m) \le \lVert v \rVert \le (\det B)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}
+% \] 
+% 
+% \vspace*{10px}
+% 
+% We have $(\det B)^{\frac{1}{4}} = (X^6N^3)^{\frac{1}{4}} < \frac{N}{\sqrt{4}}$, if we solve for $X$ this will be satisfied when
+% $X < (\frac{N}{16})^{\frac{1}{6}}$. We can consider the $\sqrt{4}$ an error term to have $X < N^{\frac{1}{6}}$.
+% With the numbers we have this inequality is verified, however even if the bound of the shortest vector is larger we still have some possibilities to
+% find the correct root.
+% 
+% Computing the root of $g(x)$ over the integers we obtain $m = \texttt{0x4142} = $ ``AB'' which is the correct result.\\
+% 
+% This specific lattice works to find roots up to size $N^{\frac{1}{6}}$, so the same construction will work if we want to find
+% 
+% \begin{itemize}
+%     \item $\approx$ 170 unkown bits of message from an RSA 1024-bit modulus
+%     \item $\approx$ 341 unkown bits of message from an RSA 2048-bit modulus
+%     \item $\approx$ 683 unkown bits of message from an RSA 4096-bit modulus
+% \end{itemize}
+% 
+% To compute bigger root a bigger lattice with more polynomials generated with \ref{eq:create_pol} is needed,
+% this method is better described in \cite{may2011} and a detailed implementation in sagemath by David Wong is available \cite{wong2015}.
+% 
+% \subsection{Factorize modulus with known MSB bits of $p$}
+% 
+% Lattices can also be used to factor a modulus $N$ knowing the most significant bits of one of the factor.
+% Let $a = 2^lb$ where $b$ are the bits known of $p$, then $p = a + r$ for some small value of $r$.
+% We can rewrite the problem to find the root $r$ of $f(x) = a + x \mod p$ such that $f(r) = p \equiv 0 \mod p$.
+% Suppose that we know the bound of $r$ such that $|r| < X$ for some bound $X$.
+% 
+% We can construct the following lattices
+% 
+% \[
+%     B = 
+%     \begin{pmatrix}
+%         X^2 & Xa & 0 \\
+%         0 & X & a \\
+%         0 & 0 & N
+%     \end{pmatrix} 
+% \]
+% 
+% \vspace*{10px}
+% 
+% Notice that the rows correspond to the polynomials $x(x + a)$, $(x + a)$, $N$ and that each of these polynomials will
+% be $0 \mod p$ when $x = r$. As before \ref{mat:lattice_rsa}, every polynomial is scaled by $X$ which is the upperbound.
+% 
+% We need to verify that the shortest vector that we can find with \textbf{LLL} will be less than $p$ because if $g(x) < p$,
+% then by construction we can compute $g(r) = 0$ over the integers.
+% In this case we have
+% 
+% \[
+%     (detB)^{\frac{1}{\dim L}} = (X^3N)^{\frac{1}{3}} < p
+% \]
+% 
+% Solving for $X$ we obtain $X < p^{\frac{1}{3}}$, so this method works for every $|r| < p^{\frac{1}{3}}$.
+% 
+% To find $r$ we just need to apply \textbf{LLL} and take the first vector (shortest) that will be of the form $v = (v_2X^2, v_1X, v_0)$.
+% 
+% The last step is to construct $g(x) = v_2x^2 + v_1x + v_0$ (just divides every coefficient by $X^i$)
+% and computes the roots over the integers to find $r$. We implemented the attack against a modulus
+% of \textbf{RSA}-$1024$ knowing the $160$ most significant bits of $p$. The attack can be expanded
+% until $X < p^{\frac{1}{2}}$ with a bigger lattice.
+
+\subsection{Real World Case Study: ROCA}
+
+\textbf{ROCA}\cite{roca} is a vulnerability discovered in 2017 in a software library \textit{RSALib}, which affects the generation of the public modulus for \textbf{RSA}.
+This issue is believed to impact millions of smart cards.
+The vulnerability arises from the method used to generate prime numbers; since embedded devices lack extensive computational resources, a rapid generation method was necessary.
+Each prime number generated adheres to the following structure:
 
@@
 
-Where $k, a$ are random values different for every prime (unkown), $g = 65537$ and $M$ it's a \textit{primorial} number.
-A \textit{primorial} number $M$ is the product of the the first $n$ successive primes
-
-\[
-    M = P_n# = \prod_{i=1}^{n} P_i
-\]
-
-where $n$ is related to key size. In the case of \textit{RSALib} the primorial number used had similar dimension to $p$,
-and the value $a, k$ didn't have much entropy. The modulus is
+Here, $k, a$ are random values unique for each prime (unknown), $g = 65537$, and $M$ is a \textit{primorial} number.
+A \textit{primorial} number $M$ is defined as the product of the first $n$ successive primes:
+
+\[
+    M = P_n\# = \prod_{i=1}^{n} P_i
+\]
+
+where $n$ corresponds to the key size. In \textit{RSALib}, the primorial number used is of similar size to $p$, and the values of $a$ and $k$ are low in entropy. The modulus is expressed as:
 
@@
 
-for $a, b, k, l \in \Z$. It's equivalent to
+for $a, b, k, l \in \Z$. This can be simplified to:
 
@@
 
-for some $c \in \Z$ since all the multiples of $kM$ or $lM$ are $0 \mod M$.
-
-It's possible to compute the discrete logarithm of $g^c \mod M$ since the size of $|M|$ is smooth with
-Pohlig-Hellman algorithm \cite{pohlig}. With $c$ we can set the bound to the value of $a$ since
+for some $c \in \Z$, as all multiples of $kM$ or $lM$ reduce to $0 \mod M$.
+
+Computing the discrete logarithm of $g^c \mod M$ is feasible due to the smoothness of $|M|$ and the effectiveness of the Pohlig-Hellman algorithm \cite{pohlig}.
+With $c$, we can establish a boundary for the value of $a$ as follows:
 
@@
 
-where $ord$ is the multiplicative order of the generator $g \in Z_M$.
-
-Once we know the bound of $a$ we can try to find the value of $k$ with the Coppersmith's method \cite{coppersmith96} for every possible $a$.
-
-The concept of the algorithm is the following:
+where $ord$ is the multiplicative order of the generator $g$ within $Z_M$.
+
+Once the bounds for $a$ are known, it becomes possible to determine the value of $k$ using Coppersmith's method \cite{coppersmith96} for each plausible $a$.
+
+The conceptual flow of the algorithm is outlined below:
 
@@
 
-In practice however the bound of $a$ is too big, so the authors found a way to move the same problem to a smaller $M'$ since the
-bitsize of $M$ are more than sufficient for making the attack works with Coppersmith's algorithm. Their optimization
-find a new $M'$ such that
+However, in practice, the bound of $a$ is too large, leading the authors to devise a method to transpose the problem to a smaller $M'$ since the bit size of $M$ is more than sufficient to make the attack viable with Coppersmith's algorithm.
+Their optimization finds a new $M'$ such that:
 
 \begin{itemize}
-    \item $(p, q)$ are still of the form \ref{eq:roca}, so $M'$ must be a divisor of $M$.
-    \item Coppersmith's algorithm will find $k'$ for the correct guess of $a'$.
-    \item Find a small order of $g \in \Z_M'$ to make $a'$ smaller.
+    \item $(p, q)$ maintain the form specified in \ref{eq:roca}, hence $M'$ must be a divisor of $M$.
+    \item Coppersmith's algorithm can determine $k'$ for the accurate guess of $a'$.
+    \item A smaller order of $g$ in $\Z_{M'}$ is found to reduce the size of $a'$.
 \end{itemize}
 
-We were able to reproduce the attack in sagemath against \textbf{RSA}-$512$, and we used as $M'$ the value
-that Bruno Produit \cite{rocaopt} made available in his thesis and David Wong's implementation of Coppersmith's attack \cite{wong2015}.
+We successfully replicated the attack in SageMath against \textbf{RSA}-$512$, using $M'$ as specified by Bruno Produit \cite{rocaopt} in his thesis and implementing David Wong's version of Coppersmith's attack \cite{wong2015}.
+
+% \subsection{Real world case study: ROCA}
+% 
+% \textbf{ROCA}\cite{roca} is a vulnerability discovered in 2017 in a software library \textit{RSALib} in the generation
+% of the public modulus for \textbf{RSA}. The attack is believed to affect millions of smart cards. The vulnerbality
+% resides in the generation of prime numbers, since embedded devices don't have lots of computational resources a fast way
+% was needed. Every prime generated has the following structure:
+% 
+% \[
+%     p = kM + (g^a \mod M)
+%     \label{eq:roca}
+% \]
+% 
+% Where $k, a$ are random values different for every prime (unkown), $g = 65537$ and $M$ it's a \textit{primorial} number.
+% A \textit{primorial} number $M$ is the product of the first $n$ successive primes 
+% 
+% \[
+%     M = P_n\# = \prod_{i=1}^{n} P_i
+% \]
+% 
+% where $n$ is related to key size. In the case of \textit{RSALib} the primorial number used had similar dimension to $p$,
+% and the value $a, k$ didn't have much entropy. The modulus is
+% 
+% \[
+%     N = (kM + g^{a}\mod M)(lM + g^{b}\mod M)
+% \]
+% 
+% for $a, b, k, l \in \Z$. It's equivalent to
+% 
+% \[
+%     N \equiv g^{a + b} \equiv g^{c} \mod M
+% \]
+% 
+% for some $c \in \Z$ since all the multiples of $kM$ or $lM$ are $0 \mod M$.
+% 
+% It's possible to compute the discrete logarithm of $g^c \mod M$ since the size of $|M|$ is smooth with
+% Pohlig-Hellman algorithm \cite{pohlig}. With $c$ we can set the bound to the value of $a$ since
+% 
+% \[
+%     \frac{c}{2} \le a \le \frac{c + ord}{2}
+% \]
+% 
+% where $ord$ is the multiplicative order of the generator $g \in Z_M$.
+% 
+% Once we know the bound of $a$ we can try to find the value of $k$ with the Coppersmith's method \cite{coppersmith96} for every possible $a$.
+% 
+% The concept of the algorithm is the following:
+% 
+% \begin{algorithm}[H]
+%     \vspace*{5px}
+%     \textbf{Input: } $N, M, g, ord, X$ \; \\
+%     $c = \log_{g}N \mod M$ \;\\
+%     \For{$a \gets (\frac{c}{2}, \frac{c + ord}{2})$}{
+%         \vspace*{5px}
+%         $f(x) = xM + (g^a \mod M)$ \; \\
+%         $g(x) = \frac{1}{M}f(x)$ [make monic, the roots are the same] \; \\
+%         $k = $ coppersmith($g(x), N, X$) [find k] \; \\ 
+%         $p = kM + (g^a \mod M)$  [candidate] \; \\
+%         \If{$N \mod p = 0$}{
+%             return $p$ \;
+%         }
+%     }
+%     \caption{Exploit idea}
+% \end{algorithm}
+% 
+% In practice however the bound of $a$ is too big, so the authors found a way to move the same problem to a smaller $M'$ since the
+% bitsize of $M$ are more than sufficient for making the attack works with Coppersmith's algorithm. Their optimization
+% find a new $M'$ such that
+% 
+% \begin{itemize}
+%     \item $(p, q)$ are still of the form \ref{eq:roca}, so $M'$ must be a divisor of $M$.
+%     \item Coppersmith's algorithm will find $k'$ for the correct guess of $a'$.
+%     \item Find a small order of $g \in \Z_M'$ to make $a'$ smaller.
+% \end{itemize}
+% 
+% We were able to reproduce the attack in sagemath against \textbf{RSA}-$512$, and we used as $M'$ the value
+% that Bruno Produit \cite{rocaopt} made available in his thesis and David Wong's implementation of Coppersmith's attack \cite{wong2015}.
 
@@
 
-\textbf{ECDSA} is a variant of the Digital Signature Algorithm (\textbf{DSA}) which uses elliptic curve cryptography.
-There are 3 public parameters:
+\textbf{ECDSA} is a variant of the Digital Signature Algorithm (\textbf{DSA}) that incorporates elliptic curve cryptography. It relies on three public parameters:
 
@@
     \item The generator point \textbf{$G$}.
-    \item The generator's order \textbf{$n$}.
+    \item The order of the generator \textbf{$n$}.
 \end{itemize}
 
-We also need to create a private key $d \in [1, n-1]$ and public key $Q = dG$. To \textbf{sign} a message $m$:
+Additionally, a private key $d \in [1, n-1]$ and a corresponding public key $Q = dG$ are required. To \textbf{sign} a message $m$:
 
 \begin{enumerate}
-    \item Compute $h = $ MSB(HASH$(m))$ where HASH is a cryptographic hash function, for example SHA-256, and MSB take the $n$ most significant bits.
+    \item Compute $h = $ MSB(HASH$(m))$, where HASH is a cryptographic hash function, such as SHA-256, and MSB extracts the $n$ most significant bits.
     \item Select a random integer $k \in [1, n-1]$ (nonce).
-    \item Calculate $P = kG = (x_1, y_1)$ and set $r = (x_1)$ if $x_1 \neq 0$, otherwise repeat the steps.
-    \item Compute $s = k^{-1}(h + dr) \mod n$, if $s = 0$ repeat the steps.
-    \item The signature is composed by $(r, s)$.
+    \item Calculate $P = kG = (x_1, y_1)$ and set $r = x_1$; if $x_1 = 0$, repeat the steps.
+    \item Compute $s = k^{-1}(h + dr) \mod n$; if $s = 0$, repeat the steps.
+    \item The signature comprises $(r, s)$.
 \end{enumerate}
 
-\vspace*{10px}
+\clearpage
 
@@
     \item Calculate $u_1 = hs^{-1} \mod n$ and $u_2 = rs^{-1} \mod n$.
-    \item Compute $P = u_1G + u_2Q = (x_1, y_1)$, if $P = O$ the signature is invalid.
-    \item If $r \equiv x_1 \mod n$ then the signature is valid.
+    \item Compute $P = u_1G + u_2Q = (x_1, y_1)$; if $P = O$, the signature is invalid.
+    \item If $r \equiv x_1 \mod n$, the signature is valid.
 \end{enumerate}
@@
 
-The security of \textbf{ECDSA} depends on the discrete logarithm problem.
-Given the points $Q, G$ such that $Q = k*G$ it's considered an hard problem to find $k$.
-However as RSA there are lots of implementation attacks
+The security of \textbf{ECDSA} hinges on the discrete logarithm problem.
+Given the points $Q$ and $G$ such that $Q = kG$, it is a challenging problem to discover $k$. However, similar to RSA, ECDSA is susceptible to various implementation attacks:
 
 \begin{itemize}
-    \item If the same $k$ is used to generate two different signatures it's possible to recover the secret key $d$. This was a real bug 
-        discovered in the Playstation 3.
-    \item It's possible to recover $d$ if the parameter $k$ is not generated with a cryptographically secure pseudo random generator.
-    \item If the elliptic curve used is not standardized (custom) then it's possible that the discrete logarithm is easily solvable
-        \cite{giuliani99attackson}, \cite{mov} \cite{smartass}.
+    \item If the same $k$ is used for generating two different signatures, it is possible to recover the private key $d$. This vulnerability was notably exploited in the PlayStation 3.
+    \item The private key $d$ can be compromised if the nonce $k$ is not produced by a cryptographically secure pseudo-random number generator.
+    \item If a non-standard (custom) elliptic curve is used, the discrete logarithm problem may become tractable, potentially undermining the security of the system \cite{giuliani99attackson}, \cite{mov}, \cite{smartass}.
 \end{itemize}
@@
 
-The lattice-based attacks presented here are based on the \textit{Hidden Number Problem} introduced
-by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significan bits
-of $k$ can potentially leak the entire nonce \cite{ecdsa_nonce}.
-
-\subsection{Recover $d$ from a pair of signatures with small $k_1, k_2$}
+The lattice-based attacks discussed here derive from the \textit{Hidden Number Problem (HNP)}, initially introduced by Boneh and Venkatesan \cite{hnp}.
+This concept was later extended to demonstrate that even partial information about the nonce $k$, specifically its most significant bits, can compromise the entire nonce \cite{ecdsa_nonce}.
+In 2020, researchers successfully extracted the most significant bits of \textit{DH} and \textit{DHE} secrets in \textbf{TLS $\le$ 1.2} and employed a lattice construction similar to the one described here to solve the \textit{HNP} and thereby breach the protocol \cite{cryptoeprint:2020:1151} (Raccoon Attack).
+
+% \chapter{ECDSA Cryptanalysis}
+% 
+% \section{ECDSA Introduction}
+% 
+% \subsection{Algorithm}
+% 
+% \textbf{ECDSA} is a variant of the Digital Signature Algorithm (\textbf{DSA}) which uses elliptic curve cryptography.
+% There are 3 public parameters:
+% 
+% \begin{itemize}
+%     \item The elliptic curve \textbf{$E$}.
+%     \item The generator point \textbf{$G$}.
+%     \item The generator's order \textbf{$n$}.
+% \end{itemize}
+% 
+% We also need to create a private key $d \in [1, n-1]$ and public key $Q = dG$. To \textbf{sign} a message $m$:
+% 
+% \begin{enumerate}
+%     \item Compute $h = $ MSB(HASH$(m))$ where HASH is a cryptographic hash function, for example SHA-256, and MSB take the $n$ most significant bits.
+%     \item Select a random integer $k \in [1, n-1]$ (nonce).
+%     \item Calculate $P = kG = (x_1, y_1)$ and set $r = (x_1)$ if $x_1 \neq 0$, otherwise repeat the steps.
+%     \item Compute $s = k^{-1}(h + dr) \mod n$, if $s = 0$ repeat the steps.
+%     \item The signature is composed by $(r, s)$.
+% \end{enumerate}
+% 
+% \clearpage
+% 
+% To \textbf{verify} the signature:
+% 
+% \begin{enumerate}
+%     \item Compute $h = $ HASH$(m)$.
+%     \item Calculate $u_1 = hs^{-1} \mod n$ and $u_2 = rs^{-1} \mod n$.
+%     \item Compute $P = u_1G + u_2Q = (x_1, y_1)$, if $P = O$ the signature is invalid.
+%     \item If $r \equiv x_1 \mod n$ then the signature is valid.
+% \end{enumerate}
+% 
+% \subsection{Security}
+% 
+% The security of \textbf{ECDSA} depends on the discrete logarithm problem.
+% Given the points $Q, G$ such that $Q = k*G$ it's considered an hard problem to find $k$.
+% However, as RSA, there are lots of implementation attacks
+% 
+% \begin{itemize}
+%     \item If the same $k$ is used to generate two different signatures it's possible to recover the secret key $d$. This was a real bug 
+%         discovered in the Playstation 3.
+%     \item It's possible to recover $d$ if the parameter $k$ is not generated with a cryptographically secure pseudo random generator.
+%     \item If the elliptic curve used is not standardized (custom) then it's possible that the discrete logarithm is easily solvable
+%         \cite{giuliani99attackson}, \cite{mov} \cite{smartass}.
+% \end{itemize}
+% 
+% \section{Lattices against ECDSA}
+% 
+% The lattice-based attacks presented here are based on the \textit{HNP (Hidden Number Problem)} introduced
+% by Boneh and Venkatesan \cite{hnp} that was in a second moment generalized to prove that the most significant bits
+% of $k$ can potentially leak the entire nonce \cite{ecdsa_nonce}.
+% In 2020 a group of researcher were able to leak the MSBs of \textit{DH} and \textit{DHE} secrets in \textbf{TLS $\le$ 1.2}
+% and used a similar lattice constructions as the one we will describe to solve the \textit{HNP}
+% and thus break the protocol \cite{cryptoeprint:2020:1151} (Raccoon Attack).
+
+% \subsection{Recover $d$ from a pair of signatures with small $k_1, k_2$}
+% 
+% \textbf{Problem setup}.
+% Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
+% $G = (\texttt{0xcc3b3d1a0c4938ef}, \\ \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.
+% 
+% We have two signature:
+% 
+% \[
+%     \begin{array}{c}
+%         (r_1, s_1) = (\texttt{0x269fa43451c5ff3c}, \texttt{0x1184ec0a74d4be7c}) \\
+%         \text{and hash } h_1 = \texttt{0xb526aef1a341cfe6}
+%     \end{array}
+% \]
+% 
+% \[
+%     \begin{array}{c}
+%         (r_2, s_2) = (\texttt{0xf77cda14f5bf50a2}, \texttt{0xcd1143ccc1516b02}) \\ 
+%         \text{and hash } h_2 = \texttt{0x84768ddee659efea}
+%     \end{array}
+% \]
+% 
+% And we know that both of these signatures use 32-bit nonce $k$, note that $n$ is a 64-bit number. We can set up the problem as a system of equation
+% 
+% \[
+%     \begin{array}{c}
+%         s_1 \equiv \displaystyle\frac{h_1 + dr_1}{k_1} \mod n \\ \\ 
+%         s_2 \equiv \displaystyle\frac{h_2 + dr_2}{k_2} \mod n
+%     \end{array}
+% \]
+% 
+% We don't know $d, k_1, k_2$, but we can write 
+% 
+% \[
+%     d = \displaystyle\frac{s_1k_1 - h_1}{r_1}
+% \]
+% 
+% and rewrite the equation in
+% 
+% \[
+%     k_1 - s_1^{-1}s_2r_1^{-1}k_2 + s_1^{-1}r_1h_2r_2^{-1} - s_1^{-1}h_1 \equiv 0 \mod n
+% \]
+% 
+% To simplify the equation we write $t = - s_1^{-1}s_2r_1^{-1}k_2$ and $u = s_1^{-1}r_1h_2r_2^{-1} - s_1^{-1}h_1$. In this way we have
+% 
+% \[
+%     \begin{array}{c}
+%         k_1 + tk_2 + u \equiv 0 \mod n \\
+%         \text{or} \\
+%         -k_1 = tk_2 + u - xn \text{   for some $x$}
+%     \end{array}
+% \]
+% 
+% We know that $|k_1|, |k_2| < K = 2^{32}$.
+% 
+% \vspace*{10px}
+% 
+% \textbf{Lattice construction}. We construct the lattice $B = (b_0, b_1, b_2)$:
+% 
+% \[
+%     B = 
+%     \begin{pmatrix}
+%         n & 0 & 0 \\
+%         t & 1 & 0 \\
+%         u & 0 & K
+%     \end{pmatrix}
+% \]
+% 
+% Note that the vector $v = (-k_1, k_2, K)$ is in the lattice because
+% 
+% \[
+%     v = -xb_0 + k_2b_1 + b_2 = (-xn + tk_2 + u = -k_1, k_2, K)
+% \]
+% 
+% for some $x, k_2 \in Z$.
+% 
+% \vspace*{10px}
+% 
+% Can we prove that $v$ is a short vector that we can find with LLL?
+% 
+% We have 
+% 
+% \begin{center}
+%     $\lVert v \rVert = \sqrt{k_1^2 + k_2^2 + K^2} \le \sqrt{3K^2} = \sqrt{3}K $
+% \end{center}
+% 
+% And we expect the shortest vector to have length
+% 
+% \[
+%     \begin{array}{c}
+%         \approx 2^{\frac{1}{2}}(\det B)^{\frac{1}{3}} \\
+%         \approx 2^{\frac{1}{2}}(nK)^{\frac{1}{3}}
+%     \end{array}
+% \]
+% 
+% So we want that 
+% 
+% \begin{center}
+%     $\lVert v \rVert \le \sqrt{3}K < \sqrt{2}(nK)^{\frac{1}{3}}$
+% \end{center}
+% 
+% And if we remove the smaller terms this will be satisfied when $K < (nK)^{\frac{1}{3}}$ or $K < \sqrt{n}$.
+% 
+% In this case if we apply LLL in the second row we obtain:
+% 
+% \begin{center}
+%     $v = (-k_1, k_2, K) = (\texttt{-0x50a65330, 0x1f5b977a, 0x100000000})$
+% \end{center}
+% 
+% To retrieve $d$ we just need to compute 
+% 
+% \[
+%     d = r_1^{-1}(k_1s_1 - h_1) = \texttt{0xf00e5fb275bfd304}
+% \]
+
+%Boneh-Venkatesan1996_Chapter_HardnessOfComputingTheMostSign-1.pdf, HPL-1999-90-1.pdf, https://www.researchgate.net/publication/2406712_The_Insecurity_of_the_Elliptic_Curve_Digital_Signature_Algorithm_with_Partially_Known_Nonces
+
+\subsection{Recover $d$ from a Pair of Signatures with Small $k_1, k_2$}
 
 \textbf{Problem setup}.
-Let $p = \texttt{0xffffffffffffd21f}$ and let $E: y^2 = x^3 + 3$ be an elliptic curve over $\F_p$ with the generator
-$G = (\texttt{0xcc3b3d1a0c4938ef}, \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.
-
-\vspace*{10px}
-
-We have two signature:
+Let $p = \texttt{0xffffffffffffd21f}$, and consider an elliptic curve $E: y^2 = x^3 + 3$ over $\F_p$ with the generator
+$G = (\texttt{0xcc3b3d1a0c4938ef}, \\ \texttt{0x4ab35ff66f8194fa})$ of order $n = \texttt{0xfffffffefa23f437}$.
+
+We analyze two signatures:
 
@@
 
-And we know that both of these signatures use 32-bit nonce $k$, note that $n$ is a 64-bit number. We can set up the problem as a system of equation
+Both signatures use a 32-bit nonce $k$, whereas $n$ is a 64-bit number. We can establish a system of equations:
 
@@
 
-We don't know $d, k_1, k_2$, but we can write
+Although $d, k_1, k_2$ are unknown, we can express:
 
@@
 
-and rewrite the equation in
+and rewrite the equation as:
 
@@
 
-To simplify the equation we write $t = - s_1^{-1}s_2r_1^{-1}k_2$ and $u = s_1^{-1}r_1h_2r_2^{-1} - s_1^{-1}h_1$. In this way we have
+To simplify, we denote $t = - s_1^{-1}s_2r_1^{-1}k_2$ and $u = s_1^{-1}r_1h_2r_2^{-1} - s_1^{-1}h_1$. This leads to:
 
@@
 
-We know that $|k_1|, |k_2| < K = 2^{32}$.
+Given that $|k_1|, |k_2| < K = 2^{32}$.
 
@@
 
-Note that the vector $v = (-k_1, k_2, K)$ is in the lattice because
+Note that the vector $v = (-k_1, k_2, K)$ lies within the lattice because:
 
@@
 
-for some $x, k_2 \in Z$.
+for some integers $x, k_2$.
 
@@
 
-Can we prove that $v$ is a short vector that we can find with LLL?
-
-We have
+Can we ascertain that $v$ is a short vector discoverable through LLL?
+
+We have:
 
@@
 
-And we expect the shortest vector to have length
+The expected length of the shortest vector is:
 
@@
 
-So we want that
+Thus, the criterion:
 
@@
 
-And if we remove the smaller terms this will be satisfied when $K < (nK)^{\frac{1}{3}}$ or $K < \sqrt{n}$.
-
-In this case if we apply LLL in the second row we obtain:
+is satisfied when $K < (nK)^{\frac{1}{3}}$ or $K < \sqrt{n}$.
+
+Applying LLL to the second row, we extract:
 
@@
 
-To retrieve $d$ we just need to compute
+To recover $d$, we compute:
 
@@
 
-Source of the method:
-
-%Boneh-Venkatesan1996_Chapter_HardnessOfComputingTheMostSign-1.pdf, HPL-1999-90-1.pdf, https://www.researchgate.net/publication/2406712_The_Insecurity_of_the_Elliptic_Curve_Digital_Signature_Algorithm_with_Partially_Known_Nonces
-
-\subsection{Recover $d$ from many signatures with small $k_i$}
-
-Suppose we have many signatures $(r_1, s_1), \ldots, (r_m, s_m)$ with message hashes $h_1, \ldots, h_m$. We can write the equivalence
-$s_i \equiv k_i^{-1}(h_i +  dr_i) \mod n$ for $i = 1,\ldots,m$ and we can remove $d$ as before to get
+\subsection{Recover $d$ from Many Signatures with Small $k_i$}
+
+Suppose we have multiple signatures $(r_1, s_1), \ldots, (r_m, s_m)$ along with their corresponding message hashes $h_1, \ldots, h_m$. We can express the relationship:
+$s_i \equiv k_i^{-1}(h_i +  dr_i) \mod n$ for $i = 1,\ldots,m$, and eliminate $d$ as previously to obtain:
 
@@
 
-And create the lattice $B$ as
+We then construct the lattice $B$ as follows:
 
@@
 
-Same as before this lattice contains $v = (-k_1, -k_2, \ldots, k_m, K)$ that can be found using LLL.
-
-\subsection{Recover $d$ knowing MSB bits of each $k_i$}
-
-What if we know the firsts MSB bits of each $k_i$?
-
-Well, we can write $k_i = (a_i + b_i)$, where $a_i$ is the known part and $b_i$ is the unkown part that satisfies $|b_i| < K$. If we plug these values
-into the equivalence we obtain
+This lattice includes the vector $v = (-k_1, -k_2, \ldots, k_m, K)$, which can be identified using LLL.
+
+\subsection{Recover $d$ Knowing MSB Bits of Each $k_i$}
+
+What if the most significant bits (MSBs) of each $k_i$ are known?
+
+In such cases, we express $k_i = (a_i + b_i)$, where $a_i$ is the known part, and $b_i$ is the unknown part satisfying $|b_i| < K$. Incorporating these values into the equivalences yields:
 
@@
 
-And we can set $u_i' = a_i + t_ia_m + u_i$ to be the value inside the lattice \ref{eq:lattice_ecdsa} instead of $u_i$. In this way the vector
+We then define $u_i' = a_i + t_ia_m + u_i$ as the new term in the lattice \ref{eq:lattice_ecdsa} in place of $u_i$. Consequently, the vector:
 
@@
 
-is in the lattice and could be found using LLL. To recover the original $(k_1, \ldots, k_m)$ we must add to $v$ the vector $w = (a_1, \ldots, a_m)$.
-
-Without any optimization we were able to recover the nonces with the $10$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures,
-but it's also possible to recover the nonces with less known bits as shown in the results obtained by Albrecht and Heninger \cite{ecdsa_result}.
+resides within the lattice and can be detected using LLL. To restore the original nonces $(k_1, \ldots, k_m)$, we simply add the vector $w = (a_1, \ldots, a_m)$ to $v$.
+
+Without specific optimizations, we successfully retrieved the nonces using only the $8$ MSB bits on the curve \texttt{secp256r1} given $100$ signatures, achieving over a $50\%$ success rate with $7$ MSB bits known.
+
+Further refinements to enhance the efficacy of this attack, allowing for fewer known bits, have been demonstrated in the findings by Albrecht and Heninger \cite{ecdsa_result}.
+
+% \subsection{Recover $d$ from many signatures with small $k_i$}
+% 
+% Suppose we have many signatures $(r_1, s_1), \ldots, (r_m, s_m)$ with message hashes $h_1, \ldots, h_m$. We can write the equivalence
+% $s_i \equiv k_i^{-1}(h_i +  dr_i) \mod n$ for $i = 1,\ldots,m$ and we can remove $d$ as before to get
+% 
+% \[
+% \begin{array}{c}
+%     k_1 + t_1k_m + u_1 \equiv 0 \mod n \\
+%     k_2 + t_2k_m + u_2 \equiv 0 \mod n \\
+%     \vdots \\
+%     k_{m-1} + t_{m-1}k_m + u_{m-1} \equiv 0 \mod n
+% \end{array}
+% \]
+% 
+% \vspace*{10px}
+% 
+% And create the lattice $B$ as
+% 
+% \[
+%     B = 
+%     \begin{pmatrix}
+%      n &  \\
+%      & n \\
+%      & & \ddots \\
+%      & & & n \\
+%      t_1 & t_2 & \cdots & t_{m-1} & 1 & 0 \\
+%      u_1 & u_2 & \cdots & u_{m-1} & 0 & K
+%      \label{eq:lattice_ecdsa}
+%     \end{pmatrix}
+% \]
+% 
+% \vspace*{10px}
+% 
+% Same as before this lattice contains $v = (-k_1, -k_2, \ldots, k_m, K)$ that can be found using LLL.
+% 
+% \subsection{Recover $d$ knowing MSB bits of each $k_i$}
+% 
+% What if we know the firsts MSB bits of each $k_i$?
+% 
+% Well, we can write $k_i = (a_i + b_i)$, where $a_i$ is the known part and $b_i$ is the unkown part that satisfies $|b_i| < K$. If we plug these values
+% into the equivalence we obtain
+% 
+% \[
+%     \begin{array}{c}
+%         k_i + t_ik_m + u_i \equiv 0 \mod n \\
+%         (a_i + b_i) + t_i(a_m + b_m) + u_i \equiv 0 \mod n \\
+%         b_i + t_ib_m + a_i + t_ia_m + u_i \equiv 0 \mod n \\
+%     \end{array}
+% \]
+% 
+% And we can set $u_i' = a_i + t_ia_m + u_i$ to be the value inside the lattice \ref{eq:lattice_ecdsa} instead of $u_i$. In this way the vector
+% 
+% \begin{center}
+%     $v = (-b_1, -b_2, \ldots, b_m, K)$
+% \end{center}
+% 
+% is in the lattice and could be found using LLL. To recover the original $(k_1, \ldots, k_m)$ we must add to $v$ the vector $w = (a_1, \ldots, a_m)$.
+% 
+% Without any optimization we were able to recover the nonces with the $8$ MSB bits known on the curve \texttt{secp256r1} given $100$ signatures 
+% and with a probability bigger than $50\%$ with $7$ MSB bits known.
+% 
+% It's possible to optimize the attack to recover the nonces with less known bits as shown in the results obtained by
+% Albrecht and Heninger \cite{ecdsa_result}.
 
@@
 
-$gg^2$
+The results from implementing these attacks are satisfactory and applicable to real-world scenarios.
+The success of these attacks often relies on a combination of probability and heuristic approaches, which are not discussed in detail here.
+As with other branches of mathematics, not all theorems and properties prove immediately useful upon their introduction.
+However, they may become valuable later, as illustrated by the Hidden Number Problem, which was crucial for the Raccoon Attack.
+
+The exploration of how to exploit side-channel attacks, such as knowing some bits of $p$ in \textbf{RSA}, has proven fruitful, as evidenced by the \textbf{ROCA} vulnerability.
+The most commonly used cryptographic protocols are generally considered secure; however, improper implementation can easily introduce vulnerabilities.
+Side-channel attacks, in particular, can significantly undermine the se
+% \chapter*{Conclusion}
+% 
+% The results obtained from the implementation of the attacks are satisfactory and can be used against real world practical cases.
+% There is a fair amount of probability and heuristic to make the attacks works that isn't discussed in detail.
+% As with other branch of mathematics not all theorems and properties are proved to be useful the moment they were first introduced
+% but can become useful years later as the hidden number problem that become crucial for the Raccoon Attack.
+% The study on how to exploit side-channel attacks (ex. knowing some bits of $p$ in \textbf{RSA}) has been proven useful
+% with \textbf{ROCA}.
+% The most used cryptographic protocol used has been proved secure but it's very easy to implement them wrong and side-channel
+% vulnerabilities can heavily compromise the security of the protocols.
 
 \bibliographystyle{plain}
-\bibliography{paper}
+
+\bibliography{lattice_based_attacks}
 
